### 2011-03-01 trunk/article/Article.tex
added document directory

%
% Complete documentation on the extended LaTeX markup used for Insight
% documentation is available in ``Documenting Insight'', which is part
% of the standard documentation for Insight.  It may be found online
% at:
%
%     http://www.itk.org/

\documentclass{InsightArticle}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  hyperref should be the last package to be loaded.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[dvips,
bookmarks,
bookmarksopen,
backref,
colorlinks,linkcolor={blue},citecolor={blue},urlcolor={blue},
]{hyperref}
% to be able to use options in graphics
\usepackage{graphicx}
% for pseudo code
\usepackage{listings}
% subfigures
\usepackage{subfigure}

%  This is a template for Papers to the Insight Journal. 
%  It is comparable to a technical report format.

% The title should be descriptive enough for people to be able to find
% the relevant document. 
\title{CITK - an architecture and examples of CUDA enabled ITK filters}

% Increment the release number whenever significant changes are made.
% The author and/or editor can define 'significant' however they like.
\release{0.00}

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Richard Beare}
\authoraddress{Richard.Beare@med.monash.edu.au\\Department of Medicine\\Monash University\\Melbourne\\Australia}

\begin{document}
\maketitle

\ifhtml
\chapter*{Front Matter\label{front}}
\fi

\begin{abstract}
\noindent
\end{abstract}

\tableofcontents

\section{Introduction}

\bibliographystyle{plain}
\bibliography{local,InsightJournal}
\nocite{ITKSoftwareGuide}

\end{document}

### 2011-04-18 trunk/Examples/Architecture1/src/AddConstantToImageFilter/CudaAddConstantToImageFilter.h
added example sources

@@ -1,0 +1,121 @@
+/*=========================================================================
+
+  Program:   Cuda Insight Toolkit
+  Module:    $RCSfile: itkCudaAddConstantToImageFilter.h,v $
+  Language:  C++ & CUDA
+  Date:      $Date: 2009-02-24 14:18:00 $
+  Version:   $Revision: 1.0 $
+
+  Copyright (c) 2010, Victorian Partnership for Advanced Computing
+All rights reserved.
+
+THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" AND
+ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED
+WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
+DISCLAIMED. IN NO EVENT SHALL <COPYRIGHT HOLDER> BE LIABLE FOR ANY
+DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
+(INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES;
+LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND
+ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+=========================================================================*/
+
+
+#ifndef __itkCudaAddConstantToImageFilter_h
+#define __itkCudaAddConstantToImageFilter_h
+
+#include "itkImageToImageFilter.h"
+
+namespace itk
+{
+  
+/** \class CudaAddConstantToImageFilter
+ *
+ * \brief Add a constant to all input pixels.
+ *
+ * This filter is templated over the input image type
+ * and the output image type.
+ *
+ * \author Phillip Ward, Victorian Partnership for Advanced Computing (VPAC)
+ *
+ * \ingroup IntensityImageFilters  CudaEnabled
+ *
+ * \sa ImageToImageFilter
+ */
+
[…]

### 2011-04-18 trunk/Examples/Architecture1/src/BackUpCudaFunctions/CudaNeighborhoodFunctions.cu

@@ -1,0 +1,191 @@
+/*
+ * File Name:    Cuda NeighboorHood Functions
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Wednesday, February 23 2010, 16:35
+ * 
+ * File Description:
+ *
+ * Used with caution, block size must be monitored for registers
+ *  and shared memory limitations.
+ *
+ * imageDim refers to the dimensions of the image.
+ * radius refers to the radius in each dimensions.
+ * pixel refers to the coordinates of the pixel that thread
+ * corresponds to.
+ * window refers to the window of shared memory. It is typically
+ * 2 * radius + blockDim in each dimension.
+ *
+ *
+ *
+ */
+#include "EclipseCompat.h"
+#include <stdio.h>
+#include <cuda.h>
+#include <cutil.h>
+
+template<class T>
+__device__ void PopulateSharedMem2D(T *sharedMem, texture<T, 2> texRef,
+		int2 imageDim, int2 radius, int2 pixel, int2 window) {
+	for (int j = 0; j < window.y; j += blockDim.y) {
+		for (int i = 0; i < window.x; i += blockDim.x) {
+			if ((threadIdx.x + i) < window.x && (threadIdx.y + j) < window.y) {
+				if ((pixel.y - radius.y + j) > -1 && (pixel.y - radius.y + j)
+						< imageDim.y && (pixel.x - radius.x + i) > -1
+						&& (pixel.x - radius.x + i) < imageDim.x) {
+					sharedMem[threadIdx.x + i + ((threadIdx.y + j) * window.x)]
+							= tex2D(texRef, pixel.x - radius.x + i, pixel.y
+									- radius.y + j);
+				}
+			}
+		}
+	}
+}
+
+template<class T>
+__device__ void PopulateSharedMem3D(T *sharedMem, texture<T, 3> texRef,
+		int3 imageDim, int3 radius, int3 pixel, int3 window) {
+	for (int k = 0; k < window.z; k += blockDim.z) {
+		for (int j = 0; j < window.y; j += blockDim.y) {
+			for (int i = 0; i < window.x; i += blockDim.x) {
[…]

### 2011-04-18 trunk/Examples/Architecture1/src/BackUpCudaFunctions/CudaTextureFunctions.cu

@@ -1,0 +1,52 @@
+/*
+ * File Name:    Cuda Texture Functions
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Wednesday, February 23 2010, 16:35
+ * 
+ * File Description:
+ *
+ */
+#include "EclipseCompat.h"
+#include <stdio.h>
+#include <cuda.h>
+#include <cutil.h>
+
+void copy3DHostToArray(float *_src, cudaArray *_dst, cudaExtent copy_extent, cudaPos src_offset, int3 imageDim)
+{
+ cudaMemcpy3DParms copyParams = {0};
+ float *h_source = _src + src_offset.x + src_offset.y*imageDim.x + src_offset.z*imageDim.x*imageDim.y;
+ copyParams.srcPtr = make_cudaPitchedPtr((void*)h_source, imageDim.x*sizeof(float), imageDim.x, imageDim.y);
+ copyParams.dstArray = _dst;
+ copyParams.kind = cudaMemcpyHostToDevice;
+ copyParams.extent = copy_extent;
+
+ CUDA_SAFE_CALL(cudaMemcpy3D(&copyParams));
+ CUT_CHECK_ERROR("Host -> Array Memcpy failed\n");
+}
+
+void copy3DDeviceToArray(float *_src, cudaArray *_dst, cudaExtent copy_extent, cudaPos src_offset, int3 imageDim)
+{
+ cudaMemcpy3DParms copyParams = {0};
+ float *d_source = _src + src_offset.x + src_offset.y*imageDim.x + src_offset.z*imageDim.x*imageDim.y;
+ copyParams.srcPtr = make_cudaPitchedPtr((void*)d_source, imageDim.x*sizeof(float), imageDim.x, imageDim.y);
+ copyParams.dstArray = _dst;
+ copyParams.kind = cudaMemcpyDeviceToDevice;
+ copyParams.extent = copy_extent;
+
+ CUDA_SAFE_CALL(cudaMemcpy3D(&copyParams));
+ CUT_CHECK_ERROR("Device -> Array Memcpy failed\n");
+}
+
+void copy3DMemToArray(cudaPitchedPtr _src, cudaArray *_dst, int3 imageDim)
+{
+ cudaMemcpy3DParms copyParams = {0};
+ copyParams.srcPtr =  _src;
[…]

### 2011-04-18 trunk/Examples/Architecture1/src/DivideByConstantImageFilter/CudaDivideByConstantImageFilterKernel.h

@@ -1,0 +1,12 @@
+/*
+ * File Name:    cuda-kernel.h
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Thursday, January 14 2010, 15:58
+ * 
+ * File Description:
+ *
+ */
+float * DivideByConstantImageKernelFunction(const float* input1, unsigned int N, float C);
+

### 2011-04-18 trunk/Examples/Architecture1/src/DivideImageFilter/CudaDivideImageFilter.h

@@ -1,0 +1,128 @@
+/*=========================================================================
+
+  Program:   Cuda Insight Toolkit
+  Module:    $RCSfile: itkCudaDivideImageFilter.h,v $
+  Language:  C++ & CUDA
+  Date:      $Date: 2009-02-24 14:18:00 $
+  Version:   $Revision: 1.0 $
+
+  Copyright (c) 2010, Victorian Partnership for Advanced Computing
+All rights reserved.
+
+THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" AND
+ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED
+WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
+DISCLAIMED. IN NO EVENT SHALL <COPYRIGHT HOLDER> BE LIABLE FOR ANY
+DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
+(INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES;
+LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND
+ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+=========================================================================*/
+
+
+#ifndef __itkCudaDivideImageFilter_h
+#define __itkCudaDivideImageFilter_h
+
+#include "itkImageToImageFilter.h"
+
+namespace itk
+{
+  
+/** \class CudaDivideImageFilter
+ * \brief Implements an operator for pixel-wise division of two images.
+ *
+ * This class is parametrized over the types of the two
+ * input images and the type of the output image. When the divisor is zero,
+ * the division result is set to the maximum number that can be represneted  by default to
+ * avoid exception. Numeric conversions (castings) are done by the C++ defaults.
+ *
[…]

### 2011-04-18 trunk/Examples/Architecture1/src/DivideImageFilter/CudaDivideImageFilterKernel.h

@@ -1,0 +1,12 @@
+/*
+ * File Name:    cuda-kernel.h
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Thursday, January 14 2010, 15:58
+ * 
+ * File Description:
+ *
+ */
+float * DivideImageKernelFunction(const float* input1, const float* input2, unsigned int N, float MAX);
+

### 2011-04-18 trunk/Examples/Architecture1/src/FilterTemplate/CudaFilterKernel.cu

@@ -1,0 +1,59 @@
+/*
+ * File Name:    cuda-kernel.cu
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Wednesday, December 23 2009, 16:35 
+ * 
+ * File Description:
+ *
+ */
+#include <stdio.h>
+#include <cuda.h>
+#include <cutil.h>
+
+template <class T>
+__global__ void cuKernel(T *output, int N)
+{
+   int idx = blockIdx.x * blockDim.x + threadIdx.x;
+   if (idx<N) 
+   {
+      // Do Something Here
+   }
+}
+
+float * cuFunction(const float* input, unsigned int N)
+{
+   float *output;
+
+   // Method #1 - Re-use Device Memory for Output
+   //
+   // Cast input to non const.
+   // Note: ContainerManageDevice must be set to false in input container.
+   // eg: 
+   /*
+      output = const_cast<float*>(input);
+   */
+
+   // Method #2 - Allocate New Memory for Output
+   //
+   // CudaMalloc new output memory
+   // Note: ContainerManageDevice must be set to true in input container.
+   // 
+   // eg: 
+   /* 
+      cudaMalloc((void **) &output, sizeof(float)*N);
+   */
+
+
+   // Compute execution configuration 
+   int blockSize = 64;
+   int nBlocks = N/blockSize + (N%blockSize == 0?0:1);
+
+
+   // Call kernal
+   cuKernel <<< nBlocks, blockSize >>> (output, N);
+
+   // Return pointer to the output
+   return output;
+}

### 2011-04-18 trunk/Examples/Architecture1/src/GrayscaleDilateImageFilter/CudaGrayscaleDilateImageFilterKernel.h

@@ -1,0 +1,15 @@
+/*
+ * File Name:    cuda-kernel.h
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Thursday, January 14 2010, 15:58
+ * 
+ * File Description:
+ *
+ */
+float * CudaGrayscaleDilateImageFilterKernelFunction(const float* input,
+				const unsigned long * imageDim, const unsigned long * radius,
+				const float * kernel, const unsigned long * kernelDim, const float zero,
+				unsigned long D, unsigned long N);
+

### 2011-04-18 trunk/Examples/Architecture1/src/GrayscaleErodeImageFilter/CudaGrayscaleErodeImageFilter.h

@@ -1,0 +1,144 @@
+/*=========================================================================
+
+  Program:   Cuda Insight Toolkit
+  Module:    $RCSfile: itkCudaGrayscaleErodeImageFilter.h,v $
+  Language:  C++ & CUDA
+  Date:      $Date: 2009-02-24 14:18:00 $
+  Version:   $Revision: 1.0 $
+
+  Copyright (c) 2010, Victorian Partnership for Advanced Computing
+All rights reserved.
+
+THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" AND
+ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED
+WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
+DISCLAIMED. IN NO EVENT SHALL <COPYRIGHT HOLDER> BE LIABLE FOR ANY
+DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
+(INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES;
+LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND
+ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+=========================================================================*/
+
+
+#ifndef __itkCudaGrayscaleErodeImageFilter_h
+#define __itkCudaGrayscaleErodeImageFilter_h
+
+#include "itkImageToImageFilter.h"
+#include "itkNeighborhood.h"
+
+namespace itk {
+
+/** \class CudaGrayscaleErodeImageFilter
+ * \brief gray scale erosion of an image
+ *
+ * Erode an image using grayscale morphology. Erosion takes the
+ * minimum of all the pixels identified by the structuring element.
+ *
+ * The structuring element is assumed to be composed of binary
+ * values (zero or one). Only elements of the structuring element
[…]

### 2011-04-18 trunk/Examples/Architecture1/src/GrayscaleMorphologicalClosingImageFilter/CudaGrayscaleMorphologicalClosingImageFilter.h

@@ -1,0 +1,120 @@
+/*=========================================================================
+
+  Program:   Cuda Insight Toolkit
+  Module:    $RCSfile: itkCudaGrayscaleMorphologicalClosingImageFilter.h,v $
+  Language:  C++ & CUDA
+  Date:      $Date: 2009-02-24 14:18:00 $
+  Version:   $Revision: 1.0 $
+
+  Copyright (c) 2010, Victorian Partnership for Advanced Computing
+All rights reserved.
+
+THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" AND
+ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED
+WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
+DISCLAIMED. IN NO EVENT SHALL <COPYRIGHT HOLDER> BE LIABLE FOR ANY
+DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
+(INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES;
+LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND
+ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+=========================================================================*/
+
+
+#ifndef __itkCudaGrayscaleMorphologicalClosingImageFilter_h
+#define __itkCudaGrayscaleMorphologicalClosingImageFilter_h
+
+#include "itkImageToImageFilter.h"
+#include "itkProgressAccumulator.h"
+#include "CudaGrayscaleDilateImageFilter.h"
+#include "CudaGrayscaleErodeImageFilter.h"
+
+namespace itk {
+
+/**
+ * \class CudaGrayscaleMorphologicalClosingImageFilter
+ * \brief gray scale morphological closing of an image.
+ *
+ * This filter removes small (i.e., smaller than the structuring
[…]

### 2011-04-18 trunk/Examples/Architecture1/src/MaximumImageFilter/CudaMaximumImageFilterKernel.cu

@@ -1,0 +1,44 @@
+/*
+ * File Name:    cuda-kernel.cu
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Wednesday, December 23 2009, 16:35 
+ * 
+ * File Description:
+ *
+ */
+#include <stdio.h>
+#include <cuda.h>
+#include <cutil.h>
+
+template <class T, class S>
+__global__ void MaximumImageKernel(T *output, const S *input, int N)
+{
+   int idx = blockIdx.x * blockDim.x + threadIdx.x;
+   if (idx<N) 
+   {
+	   S inputValue = input[idx];
+      if (output[idx] < inputValue)
+      {
+         output[idx] = inputValue;
+      }
+   }
+}
+
+float * MaximumImageKernelFunction(const float* input1, const float* input2, unsigned int N)
+{
+   float *output;
+
+   output = const_cast<float*>(input1);
+
+   // Compute execution configuration 
+   int blockSize = 128;
+   int nBlocks = N/blockSize + (N%blockSize == 0?0:1);
+
+   // Call kernal
+   MaximumImageKernel <<< nBlocks, blockSize >>> (output, input2, N);
+
+   // Return pointer to the output
+   return output;
+}

### 2011-04-18 trunk/Examples/Architecture1/src/MaximumImageFilter/CudaMaximumImageFilterKernel.h

@@ -1,0 +1,12 @@
+/*
+ * File Name:    cuda-kernel.h
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Thursday, January 14 2010, 15:58
+ * 
+ * File Description:
+ *
+ */
+float * MaximumImageKernelFunction(const float* input1, const float* input2, unsigned int N);
+

### 2011-04-18 trunk/Examples/Architecture1/src/MeanImageFilter/CudaMeanImageFilter.h

@@ -1,0 +1,114 @@
+/*=========================================================================
+
+  Program:   Cuda Insight Toolkit
+  Module:    $RCSfile: itkCudaMeanmImageFilter.h,v $
+  Language:  C++ & CUDA
+  Date:      $Date: 2009-02-24 14:18:00 $
+  Version:   $Revision: 1.0 $
+
+  Copyright (c) 2010, Victorian Partnership for Advanced Computing
+All rights reserved.
+
+THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" AND
+ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED
+WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
+DISCLAIMED. IN NO EVENT SHALL <COPYRIGHT HOLDER> BE LIABLE FOR ANY
+DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
+(INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES;
+LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND
+ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+=========================================================================*/
+
+
+#ifndef __itkCudaMeanImageFilter_h
+#define __itkCudaMeanImageFilter_h
+
+#include "itkImageToImageFilter.h"
+
+namespace itk {
+
+/** \class CudaMeanImageFilter
+ * \brief Applies an averaging filter to an image
+ *
+ * Computes an image where a given pixel is the mean value of the
+ * the pixels in a neighborhood about the corresponding input pixel.
+ *
+ * A mean filter is one of the family of linear filters.
+ *
+ * \author Phillip Ward, Victorian Partnership for Advanced Computing (VPAC)
+ *
[…]

### 2011-04-18 trunk/Examples/Architecture1/src/MeanImageFilter/CudaMeanImageFilterKernel.cu

@@ -1,0 +1,265 @@
+/*
+ * File Name:    cuda-kernel.cu
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Wednesday, December 23 2009, 16:35 
+ * 
+ * File Description:
+ *
+ */
+#include "EclipseCompat.h"
+#include <stdio.h>
+#include <iostream>
+#include <cuda.h>
+#include <cutil.h>
+#include "CudaNeighborhoodFunctions.cu"
+
+// Pointer to shared memory window
+extern __shared__ float sharedMem[];
+// Pointer to 2D Texture
+texture<float, 2> texRef2D;
+// Pointer to 3D Texture
+texture<float, 3> texRef3D;
+
+template<class T>
+__global__ void CudaMeanImageFilterKernelShared2D(T *output, int2 imageDim,
+		int2 radius, int N) {
+
+	// Compute pixel coordinates of thread
+	int2 pixel = make_int2((blockIdx.x * blockDim.x) + threadIdx.x, (blockIdx.y
+			* blockDim.y) + threadIdx.y);
+
+	// Compute window size for shared memory
+	int2 window = make_int2((2 * radius.x) + blockDim.x, (2 * radius.y)
+			+ blockDim.y);
+
+	// Populate shared memory window
+	PopulateSharedMem2D(sharedMem, texRef2D, imageDim, radius, pixel, window);
+
+	T mean = 0;
+	// Sync threads to ensure window is completely populated
+	__syncthreads();
+
+	// Returns each value in neighborhood
+	for (int j = 0; j <= 2 * radius.y; ++j) {
+		for (int i = 0; i <= 2 * radius.x; ++i) {
+			// Critical section here
+			mean += GetSharedMemValue2D(sharedMem, i, j, imageDim, radius,
+					pixel, window);
+		}
+	}
+
+	// Sync threads before doing writes to global
+	if (pixel.y < imageDim.y && pixel.x < imageDim.x) {
+		// Write value to output here
+		output[pixel.y * imageDim.x + pixel.x] = mean / ((2 * radius.x + 1)
+				* (2 * radius.y + 1));
+	}
+}
+
+template<class T>
+__global__ void CudaMeanImageFilterKernelGlobal2D(T *output, int2 imageDim,
+		int2 radius, int N, int offset) {
+
[…]

### 2011-04-18 trunk/Examples/Architecture1/src/MeanImageFilter/CudaMeanImageFilterKernel.h

@@ -1,0 +1,12 @@
+/*
+ * File Name:    cuda-kernel.h
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Thursday, January 14 2010, 15:58
+ * 
+ * File Description:
+ *
+ */
+float * CudaMeanImageFilterKernelFunction(const float* input, unsigned int imageDimX, unsigned int imageDimY, unsigned int imageDimZ,
+		unsigned int radiusX, unsigned int radiusY, unsigned int radiusZ, unsigned int N);

### 2011-04-18 trunk/Examples/Architecture1/src/MultiplyByConstantImageFilter/CudaMultiplyByConstantImageFilter.h

@@ -1,0 +1,122 @@
+/*=========================================================================
+
+  Program:   Cuda Insight Toolkit
+  Module:    $RCSfile: itkCudaMultiplyByConstantImageFilter.h,v $
+  Language:  C++ & CUDA
+  Date:      $Date: 2009-02-24 14:18:00 $
+  Version:   $Revision: 1.0 $
+
+  Copyright (c) 2010, Victorian Partnership for Advanced Computing
+All rights reserved.
+
+THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" AND
+ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED
+WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
+DISCLAIMED. IN NO EVENT SHALL <COPYRIGHT HOLDER> BE LIABLE FOR ANY
+DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
+(INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES;
+LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND
+ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+=========================================================================*/
+
+
+#ifndef __itkCudaMultiplyByConstantImageFilter_h
+#define __itkCudaMultiplyByConstantImageFilter_h
+
+#include "itkImageToImageFilter.h"
+
+namespace itk
+{
+  
+/** \class CudaMultiplyByConstantImageFilter
+ *
+ * \brief Multiply input pixels by a constant.
+ *
+ * This filter is templated over the input image type
+ * and the output image type.
+ *
+ * \author Phillip Ward, Victorian Partnership for Advanced Computing (VPAC)
+ *
+ * \ingroup IntensityImageFilters  CudaEnabled
+ *
[…]

### 2011-04-18 trunk/Examples/Architecture1/src/MultiplyByConstantImageFilter/CudaMultiplyByConstantImageFilterKernel.cu

@@ -1,0 +1,40 @@
+/*
+ * File Name:    cuda-kernel.cu
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Wednesday, December 23 2009, 16:35 
+ * 
+ * File Description:
+ *
+ */
+#include <stdio.h>
+#include <cuda.h>
+#include <cutil.h>
+
+#include "CudaMultiplyByConstantImageFilterKernel.h"
+
+template <class T>
+__global__ void MultiplyByConstantImageKernel(T *output, int N, T C) {
+	int idx = blockIdx.x * blockDim.x + threadIdx.x;
+	if (idx < N) {
+		output[idx] *= C;
+	}
+}
+
+CITK_OUT * MultiplyByConstantImageKernelFunction(const CIT_IN1* input1,
+		unsigned int N, CITK_IN1 C) {
+	CITK_OUT *output;
+
+	output = const_cast<CITK_IN1*> (input1);
+
+	// Compute execution configuration
+	int blockSize = 128;
+	int nBlocks = N / blockSize + (N % blockSize == 0 ? 0 : 1);
+
+	// Call kernel
+	MultiplyByConstantImageKernel <<< nBlocks, blockSize >>> (output, N, C);
+
+	// Return pointer to the output
+	return output;
+}

### 2011-04-18 trunk/Examples/Architecture1/src/MultiplyImageFilter/CudaMultiplyImageFilterKernel.cu

@@ -1,0 +1,57 @@
+/*
+ * File Name:    cuda-kernel.cu
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Wednesday, December 23 2009, 16:35 
+ * 
+ * File Description:
+ *
+ */
+#include <stdio.h>
+#include <cuda.h>
+#include <cutil.h>
+
+template <class T, class S>
+__global__ void multiplyImage(T *output, const S *input, int N)
+{
+   int idx = blockIdx.x * blockDim.x + threadIdx.x;
+   if (idx<N) 
+   {
+      output[idx] *= input[idx];
+   }
+}
+
+template <class T, class S>
+S * MultiplyImageKernelFunction(const T* input1, const T* input2, unsigned int N)
+{
+   S *output;
+
+   output = const_cast<S*>(input1);
+
+   // Compute execution configuration 
+   int blockSize = 128;
+   int nBlocks = N/blockSize + (N%blockSize == 0?0:1);
+
+   // Call kernel
+   multiplyImage <<< nBlocks, blockSize >>> (output, input2, N);
+
+   // Return pointer to the output
+   return output;
+}
+
+// versions we wish to compile
+#define THISTYPE float
+template THISTYPE *  MultiplyImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, const THISTYPE * input2, unsigned int N);
+#undef THISTYPE
+#define THISTYPE int
+template THISTYPE *  MultiplyImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, const THISTYPE * input2, unsigned int N);
+#undef THISTYPE
+
+#define THISTYPE short
+template THISTYPE *  MultiplyImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, const THISTYPE * input2, unsigned int N);
+#undef THISTYPE
+
+#define THISTYPE char
+template THISTYPE *  MultiplyImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, const THISTYPE * input2, unsigned int N);
+#undef THISTYPE

### 2011-04-18 trunk/Examples/Architecture1/src/NeighborhoodFilter/CudaNeighborhoodFilter.h

@@ -1,0 +1,83 @@
+/*
+ * File Name:    CudaNeighborhoodFilter.h
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Monday, January 11 2010, 16:29
+ * 
+ * File Description:
+ *
+ */
+
+#ifndef __itkCudaNeighborhoodFilter_h
+#define __itkCudaNeighborhoodFilter_h
+
+#include "itkImageToImageFilter.h"
+
+namespace itk {
+
+/** \class CudaNeighborhoodFilter
+ * \brief Computes the ABS(x) pixel-wise
+ * 
+ * \ingroup IntensityImageFilters  Multithreaded
+ */
+
+template<class TInputImage, class TOutputImage>
+class ITK_EXPORT CudaNeighborhoodFilter: public ImageToImageFilter<TInputImage,
+		TOutputImage> {
+public:
+
+	typedef TInputImage InputImageType;
+	typedef TOutputImage OutputImageType;
+
+	/** Standard class typedefs. */
+	typedef CudaNeighborhoodFilter Self;
+	typedef ImageToImageFilter<TInputImage, TOutputImage> Superclass;
+	typedef SmartPointer<Self> Pointer;
+	typedef SmartPointer<const Self> ConstPointer;
+
+	/** Method for creation through the object factory. */
+	itkNewMacro(Self)
+	;
+
+	/** Runtime information support. */
+	itkTypeMacro(CudaNeighborhoodFilter,
+			ImageToImageFilter)
+	;
+
+	typedef typename InputImageType::PixelType InputPixelType;
+	typedef typename OutputImageType::PixelType OutputPixelType;
+
+	typedef typename InputImageType::RegionType InputImageRegionType;
+	typedef typename OutputImageType::RegionType OutputImageRegionType;
+
+	typedef typename InputImageType::SizeType InputSizeType;
+
+	/** Set the radius of the neighborhood used to compute the mean. */
+	itkSetMacro(Radius, InputSizeType)
+	;
+
+	/** Get the radius of the neighborhood used to compute the mean */
+	itkGetConstReferenceMacro(Radius, InputSizeType)
+	;
+
+protected:
+	CudaNeighborhoodFilter();
+	~CudaNeighborhoodFilter() {
+	}
+	void PrintSelf(std::ostream& os, Indent indent) const;
+	void GenerateData();
+
+private:
[…]

### 2011-04-18 trunk/Examples/Architecture1/src/RescaleIntensityImageFilter/CudaRescaleIntensityImageFilter.h

@@ -1,0 +1,136 @@
+/*=========================================================================
+
+  Program:   Cuda Insight Toolkit
+  Module:    $RCSfile: itkCudaRescaleIntensityImageFilter.h,v $
+  Language:  C++ & CUDA
+  Date:      $Date: 2009-02-24 14:18:00 $
+  Version:   $Revision: 1.0 $
+
+  Copyright (c) 2010, Victorian Partnership for Advanced Computing
+All rights reserved.
+
+THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" AND
+ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED
+WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
+DISCLAIMED. IN NO EVENT SHALL <COPYRIGHT HOLDER> BE LIABLE FOR ANY
+DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
+(INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES;
+LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND
+ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+=========================================================================*/
+
+
+#ifndef __itkCudaRescaleIntensityImageFilter_h
+#define __itkCudaRescaleIntensityImageFilter_h
+
+#include "itkImageToImageFilter.h"
+
+namespace itk
+{
+  
+/** \class CudaRescaleIntensityImageFilter
+ * \brief Applies a linear transformation to the intensity levels of the
+ * input Image.
+ *
+ * RescaleIntensityImageFilter applies pixel-wise a linear transformation
+ * to the intensity values of input image pixels. The linear transformation
+ * is defined by the user in terms of the minimum and maximum values that
+ * the output image should have.
+ *
[…]

### 2011-04-18 trunk/Examples/Architecture1/src/RescaleIntensityImageFilter/CudaRescaleIntensityImageFilterKernel.h

@@ -1,0 +1,12 @@
+/*
+ * File Name:    cuda-kernel.h
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Thursday, January 14 2010, 15:58
+ * 
+ * File Description:
+ *
+ */
+float * CudaRescaleIntensityKernelFunction(const float* input, unsigned int N, float outputMax, float outputMin);
+

### 2011-04-18 trunk/Examples/Architecture1/src/StatisticsImageFilter/CudaStatisticsImageFilter.h

@@ -1,0 +1,174 @@
+/*=========================================================================
+
+  Program:   Cuda Insight Toolkit
+  Module:    $RCSfile: itkCudaStatisticsImageFilter.h,v $
+  Language:  C++ & CUDA
+  Date:      $Date: 2009-02-24 14:18:00 $
+  Version:   $Revision: 1.0 $
+
+  Copyright (c) 2010, Victorian Partnership for Advanced Computing
+All rights reserved.
+
+THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" AND
+ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED
+WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
+DISCLAIMED. IN NO EVENT SHALL <COPYRIGHT HOLDER> BE LIABLE FOR ANY
+DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
+(INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES;
+LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND
+ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+=========================================================================*/
+
+
+#ifndef __itkCudaStatisticsImageFilter_h
+#define __itkCudaStatisticsImageFilter_h
+
+#include "itkImageToImageFilter.h"
+#include "itkNumericTraits.h"
+#include "itkSimpleDataObjectDecorator.h"
+
+namespace itk {
+
+/** \class CudaStatisticsImageFilter
+ * \brief Compute min. max, variance and mean of an Image.
+ *
+ * StatisticsImageFilter computes the minimum, maximum, sum, mean, variance
+ * sigma of an image.  The filter needs all of its input image.  It
+ * behaves as a filter with an input and output. Thus it can be inserted
[…]

### 2011-04-18 trunk/Examples/Architecture1/src/StatisticsImageFilter/CudaStatisticsImageFilterKernel.cu

@@ -1,0 +1,110 @@
+/*
+ * File Name:    cuda-kernel.cu
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Wednesday, December 23 2009, 16:35 
+ * 
+ * File Description:
+ *
+ */
+#include <stdio.h>
+#include <cuda.h>
+#include <math.h>
+#include <cutil.h>
+#include "CudaStatisticsImageFilterKernel.h"
+
+__global__ void StatisticsImageKernel(float *output, float* maxImage,
+		float* minImage, float* sumImage, float* sumOfSquaresImage) {
+
+	   int idx = threadIdx.x;
+
+	   for (float offset = blockDim.x / 2 ; offset >= 1; offset /= 2)
+	   {
+	       if (idx < offset)  {
+	    	   int next = (int)(idx + offset);
+	       		maxImage[idx] = (maxImage[idx] > maxImage[next] ? maxImage[idx] : maxImage[next]);
+	       		minImage[idx] = (minImage[idx] < minImage[next] ? minImage[idx] : minImage[next]);
+	       		sumImage[idx] += sumImage[next];
+	       		sumOfSquaresImage[idx] += sumOfSquaresImage[next];
+	       }
+	       __syncthreads();
+	   }
+
+	   if (blockIdx.x == 0)
+	   {
+		   for (float offset = gridDim.x / 2 ; offset >= 1; offset /= 2)
+		   {
+		       if (idx < offset)  {
+		    	   int next = (int)(idx + offset) * blockDim.x;
+		       		maxImage[idx * blockDim.x] = (maxImage[idx * blockDim.x] > maxImage[next] ? maxImage[idx * blockDim.x] : maxImage[next]);
+		       		minImage[idx * blockDim.x] = (minImage[idx * blockDim.x] < minImage[next] ? minImage[idx * blockDim.x] : minImage[next]);
+		       		sumImage[idx * blockDim.x] += sumImage[next];
+		       		sumOfSquaresImage[idx * blockDim.x] += sumOfSquaresImage[next];
+		       }
+		       offset /= 2;
+		       __syncthreads();
+		   }
+	   }
+}
+
+__global__ void StatisticsSquareImageKernel(float* sumOfSquaresImage, int N) {
+
[…]

### 2011-04-18 trunk/Examples/Architecture1/src/StatisticsImageFilter/CudaStatisticsImageFilterKernel.h

@@ -1,0 +1,24 @@
+/*
+ * File Name:    cuda-kernel.h
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Thursday, January 14 2010, 15:58
+ * 
+ * File Description:
+ *
+ */
+struct StatisticsStruct
+{
+	float Count;
+	float Minimum;
+	float Maximum;
+	float Mean;
+	float Sigma;
+	float Sum;
+	float SumOfSquares;
+	float Variance;
+};
+
+float * StatisticsImageKernelFunction(const float* input, StatisticsStruct* stats, unsigned int N);
+

### 2011-04-18 trunk/Examples/Architecture1/src/timer.h

@@ -1,0 +1,91 @@
+#include <time.h>
+
+double getTime();
+
+/* from http://le-depotoir.googlecode.com/svn/trunk/misc/clock_gettime_stub.c */
+#ifdef __APPLE__
+
+#pragma weak clock_gettime
+
+#include <sys/time.h>
+#include <sys/resource.h>
+#include <mach/mach.h>
+#include <mach/clock.h>
+#include <mach/mach_time.h>
+#include <errno.h>
+#include <unistd.h>
+#include <sched.h>
+
+typedef enum {
+	CLOCK_REALTIME,
+	CLOCK_MONOTONIC,
+	CLOCK_PROCESS_CPUTIME_ID,
+	CLOCK_THREAD_CPUTIME_ID
+} clockid_t;
+
+static mach_timebase_info_data_t __clock_gettime_inf;
+
+int clock_gettime(clockid_t clk_id, struct timespec *tp) {
+	kern_return_t   ret;
+	clock_serv_t    clk;
+	clock_id_t clk_serv_id;
+	mach_timespec_t tm;
+	
+	uint64_t start, end, delta, nano;
+	
+	//task_basic_info_data_t tinfo;
+	//task_thread_times_info_data_t ttinfo;
+	//mach_msg_type_number_t tflag;
+	
+	int retval = -1;
+	switch (clk_id) {
+		case CLOCK_REALTIME:
+		case CLOCK_MONOTONIC:
+			clk_serv_id = clk_id == CLOCK_REALTIME ? CALENDAR_CLOCK : SYSTEM_CLOCK;
+			if (KERN_SUCCESS == (ret = host_get_clock_service(mach_host_self(), clk_serv_id, &clk))) {
+				if (KERN_SUCCESS == (ret = clock_get_time(clk, &tm))) {
+					tp->tv_sec  = tm.tv_sec;
+					tp->tv_nsec = tm.tv_nsec;
+					retval = 0;
+				}
+			}
+			if (KERN_SUCCESS != ret) {
+				errno = EINVAL;
+				retval = -1;
+			}
+		break;
+		case CLOCK_PROCESS_CPUTIME_ID:
+		case CLOCK_THREAD_CPUTIME_ID:
+			start = mach_absolute_time();
+			if (clk_id == CLOCK_PROCESS_CPUTIME_ID) {
+				getpid();
+			} else {
+				sched_yield();
+			}
+			end = mach_absolute_time();
+			delta = end - start;	
[…]

### 2011-04-18 Examples/Architecture1/src/AbsImageFilter/CudaAbsImageFilter.h
added example sources

@@ -1,0 +1,103 @@
+/*=========================================================================
+
+  Program:   Cuda Insight Toolkit
+  Module:    $RCSfile: itkCudaAbsImageFilter.h,v $
+  Language:  C++ & CUDA
+  Date:      $Date: 2009-02-24 14:18:00 $
+  Version:   $Revision: 1.0 $
+
+  Copyright (c) 2010, Victorian Partnership for Advanced Computing
+All rights reserved.
+
+THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" AND
+ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED
+WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
+DISCLAIMED. IN NO EVENT SHALL <COPYRIGHT HOLDER> BE LIABLE FOR ANY
+DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
+(INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES;
+LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND
+ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+=========================================================================*/
+
+
+#ifndef __itkCudaAbsImageFilter_h
+#define __itkCudaAbsImageFilter_h
+
+#include "itkImageToImageFilter.h"
+
+namespace itk
+{
+  
+/** \class CudaAbsImageFilter
+ * \brief Computes the ABS(x) pixel-wise
+ * 
+ * \author Phillip Ward, Victorian Partnership for Advanced Computing (VPAC)
+ *
+ * \ingroup IntensityImageFilters  CudaEnabled
+ *
+ * \sa ImageToImageFilter
+ */
+
+template <class TInputImage, class TOutputImage>
+class ITK_EXPORT CudaAbsImageFilter :
+    public
[…]

### 2011-04-18 Examples/Architecture1/src/AbsImageFilter/CudaAbsImageFilterKernel.cu

@@ -1,0 +1,40 @@
+/*
+ * File Name:    cuda-kernel.cu
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Wednesday, December 23 2009, 16:35 
+ * 
+ * File Description:
+ *
+ */
+#include <stdio.h>
+#include <cuda.h>
+//#include <cutil.h>
+
+template <class T>
+__global__ void AbsImageKernel(T*output, int N)
+{
+   int idx = blockIdx.x * blockDim.x + threadIdx.x;
+
+   if (idx<N) 
+   {
+	   T temp = output[idx];
+      output[idx] = (temp < 0) ? -temp : temp;
+   }
+}
+
+float * AbsImageKernelFunction(const float * input, unsigned int N)
+{
+	float * output = const_cast<float*>(input);
+
+   // Compute execution configuration 
+   int blockSize = 128;
+   int nBlocks = N/blockSize + (N%blockSize == 0?0:1);
+
+   // Call kernal
+   AbsImageKernel<<< nBlocks, blockSize >>> (output, N);
+
+   // Return pointer to the output
+   return output;
+}

### 2011-04-18 Examples/Architecture1/src/AbsImageFilter/CudaAbsImageFilterKernel.h

@@ -1,0 +1,13 @@
+/*
+ * File Name:    cuda-kernel.h
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Thursday, January 14 2010, 15:58
+ * 
+ * File Description:
+ *
+ */
+
+float * AbsImageKernelFunction(const float * input, unsigned int N);
+

### 2011-04-18 Examples/Architecture1/src/AddConstantToImageFilter/CudaAddConstantToImageFilterKernel.cu

@@ -1,0 +1,41 @@
+/*
+ * File Name:    cuda-kernel.cu
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Wednesday, December 23 2009, 16:35 
+ * 
+ * File Description:
+ *
+ */
+#include <stdio.h>
+#include <cuda.h>
+#include <cutil.h>
+
+template <class T>
+__global__ void AddConstantToImageKernel(T *output, int N, T C)
+{
+   int idx = blockIdx.x * blockDim.x + threadIdx.x;
+   if (idx<N) 
+   {
+      output[idx] += C;
+   }
+}
+
+float * AddConstantToImageKernelFunction(const float* input, unsigned int N, float C)
+{
+   float *output;
+
+   output = const_cast<float*>(input);
+
+   // Compute execution configuration 
+   int blockSize = 128;
+   int nBlocks = N/blockSize + (N%blockSize == 0?0:1);
+
+
+   // Call kernal
+   AddConstantToImageKernel <<< nBlocks, blockSize >>> (output, N, C);
+
+   // Return pointer to the output
+   return output;
+}

### 2011-04-18 Examples/Architecture1/src/AddConstantToImageFilter/CudaAddConstantToImageFilterKernel.h

@@ -1,0 +1,12 @@
+/*
+ * File Name:    cuda-kernel.h
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Thursday, January 14 2010, 15:58
+ * 
+ * File Description:
+ *
+ */
+float * AddConstantToImageKernelFunction(const float* input1, unsigned int N, float C);
+

### 2011-04-18 Examples/Architecture1/src/AddImageFilter/CudaAddImageFilter.h

@@ -1,0 +1,147 @@
+/*=========================================================================
+
+  Program:   Cuda Insight Toolkit
+  Module:    $RCSfile: itkCudaAddImageFilter.h,v $
+  Language:  C++ & CUDA
+  Date:      $Date: 2009-02-24 14:18:00 $
+  Version:   $Revision: 1.0 $
+
+  Copyright (c) 2010, Victorian Partnership for Advanced Computing
+All rights reserved.
+
+THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" AND
+ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED
+WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
+DISCLAIMED. IN NO EVENT SHALL <COPYRIGHT HOLDER> BE LIABLE FOR ANY
+DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
+(INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES;
+LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND
+ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+=========================================================================*/
+
+
+#ifndef __itkCudaAddImageFilter_h
+#define __itkCudaAddImageFilter_h
+
+#include "itkImageToImageFilter.h"
+
+namespace itk
+{
+  
+/** \class CudaAddImageFilter
+ * \brief Implements an operator for pixel-wise addition of two images.
+ *
+ * This class is parametrized over the types of the two
+ * input images and the type of the output image.
+ * Numeric conversions (castings) are done by the C++ defaults.
+ *
+ * The pixel type of the input 1 image must have a valid defintion of
+ * the operator+ with a pixel type of the image 2. This condition is
+ * required because internally this filter will perform the operation
+ *
[…]

### 2011-04-18 Examples/Architecture1/src/AddImageFilter/CudaAddImageFilterKernel.cu

@@ -1,0 +1,40 @@
+/*
+ * File Name:    cuda-kernel.cu
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Wednesday, December 23 2009, 16:35 
+ * 
+ * File Description:
+ *
+ */
+#include <stdio.h>
+#include <cuda.h>
+#include <cutil.h>
+
+template <class T, class S>
+__global__ void AddImageKernel(T *output, const S *input, int N)
+{
+   int idx = blockIdx.x * blockDim.x + threadIdx.x;
+   if (idx<N) 
+   {
+      output[idx] += input[idx];
+   }
+}
+
+float * AddImageKernelFunction(const float* input1, const float* input2, unsigned int N)
+{
+   float *output;
+
+   output = const_cast<float*>(input1);
+
+   // Compute execution configuration 
+   int blockSize = 128;
+   int nBlocks = N/blockSize + (N%blockSize == 0?0:1);
+
+   // Call kernal
+   AddImageKernel <<< nBlocks, blockSize >>> (output, input2, N);
+
+   // Return pointer to the output
+   return output;
+}

### 2011-04-18 Examples/Architecture1/src/AddImageFilter/CudaAddImageFilterKernel.h

@@ -1,0 +1,12 @@
+/*
+ * File Name:    cuda-kernel.h
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Thursday, January 14 2010, 15:58
+ * 
+ * File Description:
+ *
+ */
+float * AddImageKernelFunction(const float* input1, const float* input2, unsigned int N);
+

### 2011-04-18 Examples/Architecture1/src/BackUpNeighborhoodFilter/CudaNeighborhoodFilterKernel.cu

@@ -1,0 +1,286 @@
+/*
+ * File Name:    cuda-kernel.cu
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Wednesday, December 23 2009, 16:35 
+ * 
+ * File Description:
+ *
+ */
+#include "EclipseCompat.h"
+#include <stdio.h>
+#include <iostream>
+#include <cuda.h>
+#include <cutil.h>
+#include "CudaNeighborhoodFunctions.cu"
+
+// Pointer to shared memory window
+extern __shared__ float sharedMem[];
+// Pointer to 2D Texture
+texture<float, 2> texRef2D;
+// Pointer to 3D Texture
+texture<float, 3> texRef3D;
+
+template<class T>
+__global__ void CudaNeighborhoodFilterKernelShared2D(T *output, int2 imageDim,
+		int2 radius, int N) {
+
+	// Compute pixel coordinates of thread
+	int2 pixel = make_int2((blockIdx.x * blockDim.x) + threadIdx.x, (blockIdx.y
+			* blockDim.y) + threadIdx.y);
+
+	// Compute window size for shared memory
+	int2 window = make_int2((2 * radius.x) + blockDim.x, (2 * radius.y)
+			+ blockDim.y);
+
+	// Populate shared memory window
+	PopulateSharedMem2D(sharedMem, texRef2D, imageDim, radius, pixel, window);
+
+	// Sync threads to ensure window is completely populated
+	__syncthreads();
+
+	// Returns each value in neighborhood
+	for (int j = 0; j <= 2 * radius.y; ++j) {
+		for (int i = 0; i <= 2 * radius.x; ++i) {
+			// Add critical section here
+			GetSharedMemValue2D(sharedMem, i, j, imageDim, radius, pixel,
+					window);
+		}
+	}
+
+	// Sync threads before doing writes to global
+	if (pixel.y < imageDim.y && pixel.x < imageDim.x) {
+		// Write value to output here
+		output[pixel.y * imageDim.x + pixel.x] = 0;
+	}
+}
+
+template<class T>
+__global__ void CudaNeighborhoodFilterKernelGlobal2D(T *output, int2 imageDim,
+		int2 radius, int N, int offset) {
+
+	// Compute threads linear position
[…]

### 2011-04-18 Examples/Architecture1/src/BackUpNeighborhoodFilter/CudaNeighborhoodFilterKernel.h

@@ -1,0 +1,12 @@
+/*
+ * File Name:    cuda-kernel.h
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Thursday, January 14 2010, 15:58
+ * 
+ * File Description:
+ *
+ */
+float * CudaNeighborhoodFilterKernelFunction(const float* input, unsigned int imageDimX, unsigned int imageDimY, unsigned int imageDimZ,
+		unsigned int radiusX, unsigned int radiusY, unsigned int radiusZ, unsigned int N);

### 2011-04-18 Examples/Architecture1/src/BinaryThresholdImageFilter/CudaBinaryThresholdImageFilter.h

@@ -1,0 +1,144 @@
+/*=========================================================================
+
+  Program:   Cuda Insight Toolkit
+  Module:    $RCSfile: itkCudaBinaryThresholdImageFilter.h,v $
+  Language:  C++ & CUDA
+  Date:      $Date: 2009-02-24 14:18:00 $
+  Version:   $Revision: 1.0 $
+
+  Copyright (c) 2010, Victorian Partnership for Advanced Computing
+All rights reserved.
+
+THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" AND
+ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED
+WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
+DISCLAIMED. IN NO EVENT SHALL <COPYRIGHT HOLDER> BE LIABLE FOR ANY
+DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
+(INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES;
+LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND
+ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+=========================================================================*/
+
+#ifndef __CudaBinaryThresholdImageFilter_h
+#define __CudaBinaryThresholdImageFilter_h
+
+#include "itkImageToImageFilter.h"
+
+namespace itk
+{
+
+/** \class CudaBinaryThresholdImageFilter
+ *
+ * \brief Binarize an input image by thresholding.
+ *
+ * This filter produces an output image whose pixels
+ * are either one of two values ( OutsideValue or InsideValue ),
+ * depending on whether the corresponding input image pixels
+ * lie between the two thresholds ( LowerThreshold and UpperThreshold ).
[…]

### 2011-04-18 Examples/Architecture1/src/BinaryThresholdImageFilter/CudaBinaryThresholdImageFilterKernel.cu

@@ -1,0 +1,47 @@
+/*
+ * File Name:    cuda-kernel.cu
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Wednesday, December 23 2009, 16:35 
+ * Last Modified: Wednesday, December 23 2009, 16:35 
+ * 
+ * File Description:
+ *
+ */
+#include <stdio.h>
+#include <cuda.h>
+#include <cutil.h>
+
+template <class T>
+__global__ void binaryThreshold(T *output, T lower, T upper, T inside, T outside, int N)
+{
+   int idx = blockIdx.x * blockDim.x + threadIdx.x;
+   if (idx<N) 
+   {
+      float i = output[idx];
+      if (i>upper || i<lower)
+      {
+         output[idx] = inside;
+      }
+      else
+      {
+         output[idx] = outside;
+      }
+   }
+}
+
+float * BinaryThreshold(const float* input, float m_LowerThreshold, float m_UpperThreshold, float m_InsideValue, float m_OutsideValue, unsigned int N)
+{
+   // pointers
+   //float *output;
+   float *output = const_cast<float*>(input);
+
+   // Compute execution configuration
+   int blockSize = 128;
+   int nBlocks = N/blockSize + (N%blockSize == 0?0:1);
+
+   // Call  kernel
+   binaryThreshold <<< nBlocks, blockSize >>> (output, m_LowerThreshold, m_UpperThreshold, m_InsideValue, m_OutsideValue, N);
+
+   return output;
+}

### 2011-04-18 Examples/Architecture1/src/BinaryThresholdImageFilter/CudaBinaryThresholdImageFilterKernel.h

@@ -1,0 +1,17 @@
+/*
+ * File Name:    cuda-kernel.h
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Wednesday, December 23 2009, 16:59 
+ * Last Modified: Friday, January 15 2010, 15:18
+ * 
+ * File Description:
+ *
+ */
+//__global__ void binaryThreshold(float *output,
+//float lower, float upper, float inside, float outside, int N);
+
+float* BinaryThreshold(const float* input, float m_LowerThreshold,
+float m_UpperThreshold, float m_InsideValue, float m_OutsideValue,
+unsigned int N);
+

### 2011-04-18 Examples/Architecture1/src/CudaFunctions/CudaNeighborhoodFunctions.cu

@@ -1,0 +1,191 @@
+/*
+ * File Name:    Cuda NeighboorHood Functions
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Wednesday, February 23 2010, 16:35
+ * 
+ * File Description:
+ *
+ * Used with caution, block size must be monitored for registers
+ *  and shared memory limitations.
+ *
+ * imageDim refers to the dimensions of the image.
+ * radius refers to the radius in each dimensions.
+ * pixel refers to the coordinates of the pixel that thread
+ * corresponds to.
+ * window refers to the window of shared memory. It is typically
+ * 2 * radius + blockDim in each dimension.
+ *
+ *
+ *
+ */
+#include "EclipseCompat.h"
+#include <stdio.h>
+#include <cuda.h>
+#include <cutil.h>
+
+template<class T>
+__device__ void PopulateSharedMem2D(T *sharedMem, texture<T, 2> texRef,
+		int2 imageDim, int2 radius, int2 pixel, int2 kernelDim) {
+	for (int j = 0; j < kernelDim.y; j += blockDim.y) {
+		for (int i = 0; i < kernelDim.x; i += blockDim.x) {
+			if ((threadIdx.x + i) < kernelDim.x && (threadIdx.y + j) < kernelDim.y) {
+				if ((pixel.y - radius.y + j) > -1 && (pixel.y - radius.y + j)
+						< imageDim.y && (pixel.x - radius.x + i) > -1
+						&& (pixel.x - radius.x + i) < imageDim.x) {
+					sharedMem[threadIdx.x + i + ((threadIdx.y + j) * kernelDim.x)]
+							= tex2D(texRef, pixel.x - radius.x + i, pixel.y
+									- radius.y + j);
+				}
+			}
+		}
+	}
+}
+
+template<class T>
+__device__ void PopulateSharedMem3D(T *sharedMem, texture<T, 3> texRef,
+		int3 imageDim, int3 radius, int3 pixel, int3 kernelDim) {
+	for (int k = 0; k < kernelDim.z; k += blockDim.z) {
+		for (int j = 0; j < kernelDim.y; j += blockDim.y) {
[…]

### 2011-04-18 Examples/Architecture1/src/DivideByConstantImageFilter/CudaDivideByConstantImageFilter.h

@@ -1,0 +1,114 @@
+/*=========================================================================
+
+  Program:   Cuda Insight Toolkit
+  Module:    $RCSfile: itkCudaDivideByConstantImageFilter.h,v $
+  Language:  C++ & CUDA
+  Date:      $Date: 2009-02-24 14:18:00 $
+  Version:   $Revision: 1.0 $
+
+  Copyright (c) 2010, Victorian Partnership for Advanced Computing
+All rights reserved.
+
+THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" AND
+ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED
+WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
+DISCLAIMED. IN NO EVENT SHALL <COPYRIGHT HOLDER> BE LIABLE FOR ANY
+DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
+(INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES;
+LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND
+ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+=========================================================================*/
+
+
+#ifndef __itkCudaDivideByConstantImageFilter_h
+#define __itkCudaDivideByConstantImageFilter_h
+
+#include "itkImageToImageFilter.h"
+
+namespace itk
+{
+  
+/** \class CudaDivideByConstantImageFilter
+ *
+ * \brief Divide input pixels by a constant.
+ *
+ * This filter is templated over the input image type
+ * and the output image type.
+ *
+ * \author Phillip Ward, Victorian Partnership for Advanced Computing (VPAC)
+ *
+ * \ingroup IntensityImageFilters  CudaEnabled
+ * \sa ImageToImageFilter
+ */
[…]

### 2011-04-18 Examples/Architecture1/src/DivideByConstantImageFilter/CudaDivideByConstantImageFilterKernel.cu

@@ -1,0 +1,41 @@
+/*
+ * File Name:    cuda-kernel.cu
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Wednesday, December 23 2009, 16:35 
+ * 
+ * File Description:
+ *
+ */
+#include <stdio.h>
+#include <cuda.h>
+#include <cutil.h>
+
+template <class T>
+__global__ void DivideByConstantImageKernel(T *output, int N, T C)
+{
+   int idx = blockIdx.x * blockDim.x + threadIdx.x;
+   if (idx<N) 
+   {
+      output[idx] = output[idx] / C;
+      
+   }
+}
+
+float * DivideByConstantImageKernelFunction(const float* input1, unsigned int N, float C)
+{
+   float *output;
+
+   output = const_cast<float*>(input1);
+
+   // Compute execution configuration 
+   int blockSize = 128;
+   int nBlocks = N/blockSize + (N%blockSize == 0?0:1);
+
+   // Call kernal
+   DivideByConstantImageKernel <<< nBlocks, blockSize >>> (output, N, C);
+
+   // Return pointer to the output
+   return output;
+}

### 2011-04-18 Examples/Architecture1/src/DivideImageFilter/CudaDivideImageFilterKernel.cu

@@ -1,0 +1,42 @@
+/*
+ * File Name:    cuda-kernel.cu
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Wednesday, December 23 2009, 16:35 
+ * 
+ * File Description:
+ *
+ */
+#include <stdio.h>
+#include <cuda.h>
+#include <cutil.h>
+
+template <class T, class S>
+__global__ void DivideImageKernel(T *output, const S *input, int N, T MAX)
+{
+   int idx = blockIdx.x * blockDim.x + threadIdx.x;
+   if (idx<N) 
+   {
+      output[idx] = output[idx] / input[idx];
+      if (input[idx]==0) { output[idx] = MAX; }
+   }
+}
+
+float * DivideImageKernelFunction(const float* input1, const float* input2, unsigned int N, float MAX)
+{
+   float *output;
+
+   output = const_cast<float*>(input1);
+
+   // Compute execution configuration 
+   int blockSize = 64;
+   int nBlocks = N/blockSize + (N%blockSize == 0?0:1);
+
+
+   // Call kernal
+   DivideImageKernel <<< nBlocks, blockSize >>> (output, input2, N, MAX);
+
+   // Return pointer to the output
+   return output;
+}

### 2011-04-18 Examples/Architecture1/src/EclipseCompat.h

@@ -1,0 +1,18 @@
+/*
+** EclipseCompat.h
+**
+**  Created on: Jan 19, 2010
+**      Author: lukep
+*/
+
+#ifndef ECLIPSECOMPAT_H_
+#define ECLIPSECOMPAT_H_
+
+#ifdef __CDT_PARSER__
+#define __global__
+#define __device__
+#define __host__
+#define __shared__
+#endif
+
+#endif /* ECLIPSECOMPAT_H_ */

### 2011-04-18 Examples/Architecture1/src/FilterTemplate/CudaFilter.h

@@ -1,0 +1,93 @@
+/*=========================================================================
+
+  Program:   Cuda Insight Toolkit
+  Module:    $RCSfile: itkCudaImageFilter.h,v $
+  Language:  C++ & CUDA
+  Date:      $Date: 2009-02-24 14:18:00 $
+  Version:   $Revision: 1.0 $
+
+  Copyright (c) 2010, Victorian Partnership for Advanced Computing
+All rights reserved.
+
+THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" AND
+ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED
+WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
+DISCLAIMED. IN NO EVENT SHALL <COPYRIGHT HOLDER> BE LIABLE FOR ANY
+DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
+(INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES;
+LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND
+ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+=========================================================================*/
+
+
+#ifndef __itkCudaFilter_h
+#define __itkCudaFilter_h
+
+#include "itkImageToImageFilter.h"
+
+namespace itk
+{
+  
+/** \class CudaFilter
+ * \brief Computes the ABS(x) pixel-wise
+ * 
+ * \author Phillip Ward, Victorian Partnership for Advanced Computing (VPAC)
+ *
+ * \ingroup IntensityImageFilters  Multithreaded
+ *
+ * \sa ImageToImageFilter
+ */
+
+template <class TInputImage, class TOutputImage>
+class ITK_EXPORT CudaFilter :
+    public
+ImageToImageFilter<TInputImage, TOutputImage >
+{
+public:
+
[…]

### 2011-04-18 Examples/Architecture1/src/FilterTemplate/CudaFilterKernel.h

@@ -1,0 +1,12 @@
+/*
+ * File Name:    cuda-kernel.h
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Thursday, January 14 2010, 15:58
+ * 
+ * File Description:
+ *
+ */
+float * cuFunction(const float* input, unsigned int N);
+

### 2011-04-18 Examples/Architecture1/src/GrayscaleDilateImageFilter/CudaGrayscaleDilateImageFilter.h

@@ -1,0 +1,143 @@
+/*=========================================================================
+
+  Program:   Cuda Insight Toolkit
+  Module:    $RCSfile: itkCudaGrayscaleDilateImageFilter.h,v $
+  Language:  C++ & CUDA
+  Date:      $Date: 2009-02-24 14:18:00 $
+  Version:   $Revision: 1.0 $
+
+  Copyright (c) 2010, Victorian Partnership for Advanced Computing
+All rights reserved.
+
+THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" AND
+ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED
+WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
+DISCLAIMED. IN NO EVENT SHALL <COPYRIGHT HOLDER> BE LIABLE FOR ANY
+DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
+(INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES;
+LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND
+ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+=========================================================================*/
+
+
+#ifndef __itkCudaGrayscaleDilateImageFilter_h
+#define __itkCudaGrayscaleDilateImageFilter_h
+
+#include "itkImageToImageFilter.h"
+#include "itkNeighborhood.h"
+
+namespace itk {
+
+/**
+ * \class CudaGrayscaleDilateImageFilter
+ * \brief gray scale dilation of an image
+ *
+ * Dilate an image using grayscale morphology. Dilation takes the
+ * maximum of all the pixels identified by the structuring element.
+ *
+ * The structuring element is assumed to be composed of binary
+ * values (zero or one). Only elements of the structuring element
[…]

### 2011-04-18 Examples/Architecture1/src/GrayscaleDilateImageFilter/CudaGrayscaleDilateImageFilterKernel.cu

@@ -1,0 +1,290 @@
+/*
+ * File Name:    cuda-kernel.cu
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Wednesday, December 23 2009, 16:35 
+ * 
+ * File Description:
+ *
+ */
+#include "EclipseCompat.h"
+#include <stdio.h>
+#include <iostream>
+#include <cuda.h>
+#include <cutil.h>
+#include "CudaNeighborhoodFunctions.cu"
+
+// Pointer to 2D Texture
+texture<float, 2> texRef2DKernel;
+texture<float, 2> texRef2DInput;
+// Pointer to 3D Texture
+texture<float, 3> texRef3DKernel;
+texture<float, 3> texRef3DInput;
+
+template<class T>
+__global__ void CudaGrayscaleDilateImageFilterKernelGlobal2D(T *output,
+		int2 imageDim, int2 radius, int2 kernelDim, unsigned long N, int offset) {
+
+	// Compute threads linear position
+	unsigned int idx = blockIdx.x * blockDim.x + threadIdx.x + offset;
+
+	if (idx < N) {
+		// Compute pixel coordinates of thread
+		int2 pixel = make_int2(idx % imageDim.x, idx / imageDim.x);
+		T max = GetGlobalValue2D(texRef2DInput, radius.x+1, radius.y+1, imageDim,
+				radius, pixel);
+		T temp;
+
+		// Returns each value in neighborhood
+		for (int j = 0; j < kernelDim.y; j++) {
+			for (int i = 0; i < kernelDim.x; i++) {
+				// Add critical section here
+				if (tex2D(texRef2DKernel, i, j) > 0) {
+					temp = GetGlobalValue2D(texRef2DInput, i, j, imageDim,
+							radius, pixel);
+					max = (temp > max) ? temp : max;
+				}
+			}
+		}
+
+		// Sync before writing back to global
+		__syncthreads();
+
+		// Write output
+		output[idx] = max;
+	}
+}
+
+template<class T>
+__global__ void CudaGrayscaleDilateImageFilterKernelGlobal3D(T *output,
+		int3 imageDim, int3 radius, int3 kernelDim, unsigned long N, int offset) {
+
+	// Compute threads linear position
[…]

### 2011-04-18 Examples/Architecture1/src/GrayscaleErodeImageFilter/CudaGrayscaleErodeImageFilterKernel.cu

@@ -1,0 +1,290 @@
+/*
+ * File Name:    cuda-kernel.cu
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Wednesday, December 23 2009, 16:35 
+ * 
+ * File Description:
+ *
+ */
+#include "EclipseCompat.h"
+#include <stdio.h>
+#include <iostream>
+#include <cuda.h>
+#include <cutil.h>
+#include "CudaNeighborhoodFunctions.cu"
+
+// Pointer to 2D Texture
+texture<float, 2> texRef2DKernel;
+texture<float, 2> texRef2DInput;
+// Pointer to 3D Texture
+texture<float, 3> texRef3DKernel;
+texture<float, 3> texRef3DInput;
+
+template<class T>
+__global__ void CudaGrayscaleErodeImageFilterKernelGlobal2D(T *output,
+		int2 imageDim, int2 radius, int2 kernelDim, unsigned long N, int offset) {
+
+	// Compute threads linear position
+	unsigned int idx = blockIdx.x * blockDim.x + threadIdx.x + offset;
+
+	if (idx < N) {
+		// Compute pixel coordinates of thread
+		int2 pixel = make_int2(idx % imageDim.x, idx / imageDim.x);
+		T min = GetGlobalValue2D(texRef2DInput, radius.x+1, radius.y+1, imageDim,
+				radius, pixel);
+		T temp;
+
+		// Returns each value in neighborhood
+		for (int j = 0; j < kernelDim.y; j++) {
+			for (int i = 0; i < kernelDim.x; i++) {
+				// Add critical section here
+				if (tex2D(texRef2DKernel, i, j) > 0) {
+					temp = GetGlobalValue2D(texRef2DInput, i, j, imageDim,
+							radius, pixel);
+					min = (temp < min) ? temp : min;
+				}
+			}
+		}
+
+		// Sync before writing back to global
+		__syncthreads();
+
+		// Write output
+		output[idx] = min;
+	}
+}
+
+template<class T>
+__global__ void CudaGrayscaleErodeImageFilterKernelGlobal3D(T *output,
+		int3 imageDim, int3 radius, int3 kernelDim, unsigned long N, int offset) {
+
+	// Compute threads linear position
[…]

### 2011-04-18 Examples/Architecture1/src/GrayscaleErodeImageFilter/CudaGrayscaleErodeImageFilterKernel.h

@@ -1,0 +1,15 @@
+/*
+ * File Name:    cuda-kernel.h
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Thursday, January 14 2010, 15:58
+ * 
+ * File Description:
+ *
+ */
+float * CudaGrayscaleErodeImageFilterKernelFunction(const float* input,
+				const unsigned long * imageDim, const unsigned long * radius,
+				const float * kernel, const unsigned long * kernelDim, const float zero,
+				unsigned long D, unsigned long N);
+

### 2011-04-18 Examples/Architecture1/src/GrayscaleMorphologicalOpeningImageFilter/CudaGrayscaleMorphologicalOpeningImageFilter.h

@@ -1,0 +1,146 @@
+/*=========================================================================
+
+  Program:   Cuda Insight Toolkit
+  Module:    $RCSfile: itkCudaGrayscaleMorphologicalOpeningImageFilter.h,v $
+  Language:  C++ & CUDA
+  Date:      $Date: 2009-02-24 14:18:00 $
+  Version:   $Revision: 1.0 $
+
+  Copyright (c) 2010, Victorian Partnership for Advanced Computing
+All rights reserved.
+
+THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" AND
+ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED
+WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
+DISCLAIMED. IN NO EVENT SHALL <COPYRIGHT HOLDER> BE LIABLE FOR ANY
+DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
+(INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES;
+LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND
+ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+=========================================================================*/
+
+
+#ifndef __itkCudaGrayscaleMorphologicalOpeningImageFilter_h
+#define __itkCudaGrayscaleMorphologicalOpeningImageFilter_h
+
+#include "itkImageToImageFilter.h"
+#include "itkProgressAccumulator.h"
+#include "CudaGrayscaleDilateImageFilter.h"
+#include "CudaGrayscaleErodeImageFilter.h"
+
+namespace itk {
+
+/**
+ * \class CudaGrayscaleMorphologicalOpeningImageFilter
+ * \brief gray scale morphological opening of an image.
+ *
+ * This filter preserves regions, in the foreground, that can
[…]

### 2011-04-18 Examples/Architecture1/src/MaximumImageFilter/CudaMaximumImageFilter.h

@@ -1,0 +1,127 @@
+/*=========================================================================
+
+  Program:   Cuda Insight Toolkit
+  Module:    $RCSfile: itkCudaMaximumImageFilter.h,v $
+  Language:  C++ & CUDA
+  Date:      $Date: 2009-02-24 14:18:00 $
+  Version:   $Revision: 1.0 $
+
+  Copyright (c) 2010, Victorian Partnership for Advanced Computing
+All rights reserved.
+
+THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" AND
+ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED
+WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
+DISCLAIMED. IN NO EVENT SHALL <COPYRIGHT HOLDER> BE LIABLE FOR ANY
+DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
+(INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES;
+LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND
+ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+=========================================================================*/
+
+
+#ifndef __itkCudaMaximumImageFilter_h
+#define __itkCudaMaximumImageFilter_h
+
+#include "itkImageToImageFilter.h"
+
+namespace itk
+{
+  
+/** \class CudaMaximumImageFilter
+ * \brief Implements a pixel-wise operator Max(a,b) between two images.
+ *
+ * The pixel values of the output image are the maximum between the
+ * corresponding pixels of the two input images.
+ *
+ * This class is parametrized over the types of the two
+ * input images and the type of the output image.
+ * Numeric conversions (castings) are done by the C++ defaults.
+ *
[…]

### 2011-04-18 Examples/Architecture1/src/MinimumImageFilter/CudaMinimumImageFilter.h

@@ -1,0 +1,130 @@
+/*=========================================================================
+
+  Program:   Cuda Insight Toolkit
+  Module:    $RCSfile: itkCudaMinimumImageFilter.h,v $
+  Language:  C++ & CUDA
+  Date:      $Date: 2009-02-24 14:18:00 $
+  Version:   $Revision: 1.0 $
+
+  Copyright (c) 2010, Victorian Partnership for Advanced Computing
+All rights reserved.
+
+THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" AND
+ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED
+WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
+DISCLAIMED. IN NO EVENT SHALL <COPYRIGHT HOLDER> BE LIABLE FOR ANY
+DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
+(INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES;
+LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND
+ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+=========================================================================*/
+
+
+#ifndef __itkCudaMinimumImageFilter_h
+#define __itkCudaMinimumImageFilter_h
+
+#include "itkImageToImageFilter.h"
+
+namespace itk
+{
+  
+/** \class CudaMinimumImageFilter
+ * \brief Implements a pixel-wise operator Min(a,b) between two images.
+ *
+ * The pixel values of the output image are the minimum between the
+ * corresponding pixels of the two input images.
+ *
+ * This class is parametrized over the types of the two
+ * input images and the type of the output image.
+ * Numeric conversions (castings) are done by the C++ defaults.
+ *
[…]

### 2011-04-18 Examples/Architecture1/src/MinimumImageFilter/CudaMinimumImageFilterKernel.cu

@@ -1,0 +1,44 @@
+/*
+ * File Name:    cuda-kernel.cu
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Wednesday, December 23 2009, 16:35 
+ * 
+ * File Description:
+ *
+ */
+#include <stdio.h>
+#include <cuda.h>
+#include <cutil.h>
+
+template <class T, class S>
+__global__ void MinimumImageKernel(T *output, const S *input, int N)
+{
+   int idx = blockIdx.x * blockDim.x + threadIdx.x;
+   if (idx<N) 
+   {
+	   S inputValue = input[idx];
+   	  if (output[idx] > inputValue)
+   	  {
+      	output[idx] = inputValue;
+      }
+   }
+}
+
+float * MinimumImageKernelFunction(const float* input1, const float* input2, unsigned int N)
+{
+   float *output;
+
+   output = const_cast<float*>(input1);
+
+   // Compute execution configuration 
+   int blockSize = 128;
+   int nBlocks = N/blockSize + (N%blockSize == 0?0:1);
+
+   // Call kernel
+   MinimumImageKernel <<< nBlocks, blockSize >>> (output, input2, N);
+
+   // Return pointer to the output
+   return output;
+}

### 2011-04-18 Examples/Architecture1/src/MinimumImageFilter/CudaMinimumImageFilterKernel.h

@@ -1,0 +1,12 @@
+/*
+ * File Name:    cuda-kernel.h
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Thursday, January 14 2010, 15:58
+ * 
+ * File Description:
+ *
+ */
+float * MinimumImageKernelFunction(const float* input1, const float* input2, unsigned int N);
+

### 2011-04-18 Examples/Architecture1/src/MultiplyByConstantImageFilter/CudaMultiplyByConstantImageFilterKernel.h

@@ -1,0 +1,13 @@
+/*
+ * File Name:    cuda-kernel.h
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Thursday, January 14 2010, 15:58
+ * 
+ * File Description:
+ *
+ */
+
+CITK_OUT * MultiplyByConstantImageKernelFunction(const CITK_IN1 * input1, unsigned int N, CITK_IN1 C);
+

### 2011-04-18 Examples/Architecture1/src/MultiplyImageFilter/CudaMultiplyImageFilter.h

@@ -1,0 +1,124 @@
+/*=========================================================================
+
+  Program:   Cuda Insight Toolkit
+  Module:    $RCSfile: itkCudaMultiplyImageFilter.h,v $
+  Language:  C++ & CUDA
+  Date:      $Date: 2009-02-24 14:18:00 $
+  Version:   $Revision: 1.0 $
+
+  Copyright (c) 2010, Victorian Partnership for Advanced Computing
+All rights reserved.
+
+THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" AND
+ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED
+WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
+DISCLAIMED. IN NO EVENT SHALL <COPYRIGHT HOLDER> BE LIABLE FOR ANY
+DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
+(INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES;
+LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND
+ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+=========================================================================*/
+
+
+#ifndef __itkCudaMultiplyImageFilter_h
+#define __itkCudaMultiplyImageFilter_h
+
+#include "itkImageToImageFilter.h"
+
+namespace itk
+{
+  
+/** \class CudaMultiplyImageFilter
+ * \brief Implements an operator for pixel-wise multiplication of two images.
+ *
+ * This class is parametrized over the types of the two
+ * input images and the type of the output image.
+ * Numeric conversions (castings) are done by the C++ defaults.
+ * 
+ * \author Phillip Ward, Victorian Partnership for Advanced Computing (VPAC)
+ *
[…]

### 2011-04-18 Examples/Architecture1/src/MultiplyImageFilter/CudaMultiplyImageFilterKernel.h

@@ -1,0 +1,4 @@
+
+template <class T, class S> extern
+S * MultiplyImageKernelFunction(const T* input1, const T* input2, unsigned int N);
+

### 2011-04-18 Examples/Architecture1/src/NeighborhoodFilter/CudaNeighborhoodFilterKernel.cu

@@ -1,0 +1,286 @@
+/*
+ * File Name:    cuda-kernel.cu
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Wednesday, December 23 2009, 16:35 
+ * 
+ * File Description:
+ *
+ */
+#include "EclipseCompat.h"
+#include <stdio.h>
+#include <iostream>
+#include <cuda.h>
+#include <cutil.h>
+#include "CudaNeighborhoodFunctions.cu"
+
+// Pointer to shared memory window
+extern __shared__ float sharedMem[];
+// Pointer to 2D Texture
+texture<float, 2> texRef2D;
+// Pointer to 3D Texture
+texture<float, 3> texRef3D;
+
+template<class T>
+__global__ void CudaNeighborhoodFilterKernelShared2D(T *output, int2 imageDim,
+		int2 radius, int N) {
+
+	// Compute pixel coordinates of thread
+	int2 pixel = make_int2((blockIdx.x * blockDim.x) + threadIdx.x, (blockIdx.y
+			* blockDim.y) + threadIdx.y);
+
+	// Compute window size for shared memory
+	int2 window = make_int2((2 * radius.x) + blockDim.x, (2 * radius.y)
+			+ blockDim.y);
+
+	// Populate shared memory window
+	PopulateSharedMem2D(sharedMem, texRef2D, imageDim, radius, pixel, window);
+
+	// Sync threads to ensure window is completely populated
+	__syncthreads();
+
+	// Returns each value in neighborhood
+	for (int j = 0; j <= 2 * radius.y; ++j) {
+		for (int i = 0; i <= 2 * radius.x; ++i) {
+			// Add critical section here
+			GetSharedMemValue2D(sharedMem, i, j, imageDim, radius, pixel,
+					window);
+		}
+	}
+
+	// Sync threads before doing writes to global
+	if (pixel.y < imageDim.y && pixel.x < imageDim.x) {
+		// Write value to output here
+		output[pixel.y * imageDim.x + pixel.x] = 0;
+	}
+}
+
+template<class T>
+__global__ void CudaNeighborhoodFilterKernelGlobal2D(T *output, int2 imageDim,
+		int2 radius, int N, int offset) {
+
+	// Compute threads linear position
[…]

### 2011-04-18 Examples/Architecture1/src/RescaleIntensityImageFilter/CudaRescaleIntensityImageFilterKernel.cu

@@ -1,0 +1,100 @@
+/*
+ * File Name:    cuda-kernel.cu
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Wednesday, December 23 2009, 16:35 
+ * 
+ * File Description:
+ *
+ */
+#include <stdio.h>
+#include <cuda.h>
+#include <cutil.h>
+
+template <class T>
+__global__ void MaxMinKernel(T *maxImage, T *minImage, int N)
+{
+   int idx = blockIdx.x * blockDim.x + threadIdx.x;
+
+   float offset = N/2;   
+
+   for ( ; ((int)offset) > 0; )   
+   {
+       if (idx < offset)  {   		
+       		maxImage[idx] = (maxImage[idx] > maxImage[(int)(idx + offset)] ? maxImage[idx] : maxImage[(int)(idx + offset)]);
+       		minImage[idx] = (minImage[idx] < minImage[(int)(idx + offset)] ? minImage[idx] : minImage[(int)(idx + offset)]);
+       } else {
+       		return;
+       }
+       offset /= 2;
+       __syncthreads();
+   }
+}
+
+template <class T>
+__global__ void RescaleIntensityKernel(T *output, T offset, float factor, T max, T min, int N)
+{
+   int idx = blockIdx.x * blockDim.x + threadIdx.x;
+   
+   if (idx < N)
+   {
+	   T temp = output[idx] * factor + offset;
+   		output[idx] = (temp > max ? max : temp);
+   		output[idx] = (temp < min ? min : temp);
+   }   
+}
+
+float * CudaRescaleIntensityKernelFunction(const float* input, unsigned int N, float outputMax, float outputMin)
+{
+   float *output = const_cast<float*>(input);
+   float *maxImage, *minImage; 
+   
+   cudaMalloc((void **)&maxImage, sizeof(float)*N);
+   cudaMalloc((void **)&minImage, sizeof(float)*N);
+   
+   cudaMemcpy(maxImage, output, sizeof(float)*N, cudaMemcpyDeviceToDevice);
+   cudaMemcpy(minImage, output, sizeof(float)*N, cudaMemcpyDeviceToDevice);
+
+   // Compute execution configuration 
+   int blockSize = 256;
[…]

### 2011-04-18 Examples/Architecture1/src/SubtractConstantFromImageFilter/CudaSubtractConstantFromImageFilter.h

@@ -1,0 +1,120 @@
+/*=========================================================================
+
+  Program:   Cuda Insight Toolkit
+  Module:    $RCSfile: itkCudaSubtractConstantFromImageFilter.h,v $
+  Language:  C++ & CUDA
+  Date:      $Date: 2009-02-24 14:18:00 $
+  Version:   $Revision: 1.0 $
+
+  Copyright (c) 2010, Victorian Partnership for Advanced Computing
+All rights reserved.
+
+THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" AND
+ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED
+WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
+DISCLAIMED. IN NO EVENT SHALL <COPYRIGHT HOLDER> BE LIABLE FOR ANY
+DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
+(INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES;
+LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND
+ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+=========================================================================*/
+
+
+#ifndef __itkCudaSubtractConstantFromImageFilter_h
+#define __itkCudaSubtractConstantFromImageFilter_h
+
+#include "itkImageToImageFilter.h"
+
+namespace itk
+{
+  
+/** \class CudaSubtractConstantFromImageFilter
+ *
+ * \brief Subtract a constant from all input pixels.
+ *
+ * This filter is templated over the input image type
+ * and the output image type.
+ *
+ * \author Phillip Ward, Victorian Partnership for Advanced Computing
+ *
+ * \ingroup IntensityImageFilters CudaEnabled
+ *
[…]

### 2011-04-18 Examples/Architecture1/src/SubtractConstantFromImageFilter/CudaSubtractConstantFromImageFilterKernel.cu

@@ -1,0 +1,38 @@
+/*
+ * File Name:    cuda-kernel.cu
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Wednesday, December 23 2009, 16:35 
+ * 
+ * File Description:
+ *
+ */
+#include <stdio.h>
+#include <cuda.h>
+#include <cutil.h>
+
+template <class T>
+__global__ void SubtractConstantFromImageKernel(T *output, int N, T C) {
+	int idx = blockIdx.x * blockDim.x + threadIdx.x;
+	if (idx < N) {
+		output[idx] -= C;
+	}
+}
+
+float * SubtractConstantFromImageKernelFunction(const float* input1,
+		unsigned int N, float C) {
+	float *output;
+
+	output = const_cast<float*> (input1);
+
+	// Compute execution configuration
+	int blockSize = 128;
+	int nBlocks = N / blockSize + (N % blockSize == 0 ? 0 : 1);
+
+	// Call kernel
+	SubtractConstantFromImageKernel <<< nBlocks, blockSize >>> (output, N, C);
+
+	// Return pointer to the output
+	return output;
+}

### 2011-04-18 Examples/Architecture1/src/SubtractConstantFromImageFilter/CudaSubtractConstantFromImageFilterKernel.h

@@ -1,0 +1,12 @@
+/*
+ * File Name:    cuda-kernel.h
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Thursday, January 14 2010, 15:58
+ * 
+ * File Description:
+ *
+ */
+float * SubtractConstantFromImageKernelFunction(const float* input1, unsigned int N, float C);
+

### 2011-04-18 Examples/Architecture1/src/SubtractImageFilter/CudaSubtractImageFilter.h

@@ -1,0 +1,127 @@
+/*=========================================================================
+
+  Program:   Cuda Insight Toolkit
+  Module:    $RCSfile: itkCudaSubtractImageFilter.h,v $
+  Language:  C++ & CUDA
+  Date:      $Date: 2009-02-24 14:18:00 $
+  Version:   $Revision: 1.0 $
+
+  Copyright (c) 2010, Victorian Partnership for Advanced Computing
+All rights reserved.
+
+THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" AND
+ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED
+WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
+DISCLAIMED. IN NO EVENT SHALL <COPYRIGHT HOLDER> BE LIABLE FOR ANY
+DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
+(INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES;
+LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND
+ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+
+=========================================================================*/
+
+
+#ifndef __itkCudaSubtractImageFilter_h
+#define __itkCudaSubtractImageFilter_h
+
+#include "itkImageToImageFilter.h"
+
+namespace itk
+{
+  
+/** \class CudaSubtractImageFilter
+ * \brief Implements an operator for pixel-wise subtraction of two images.
+ *
+ * Output = Input1 - Input2.
+ * 
+ * This class is parametrized over the types of the two
+ * input images and the type of the output image.
+ * Numeric conversions (castings) are done by the C++ defaults.
+ *
[…]

### 2011-04-18 Examples/Architecture1/src/SubtractImageFilter/CudaSubtractImageFilterKernel.cu

@@ -1,0 +1,40 @@
+/*
+ * File Name:    cuda-kernel.cu
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Wednesday, December 23 2009, 16:35 
+ * 
+ * File Description:
+ *
+ */
+#include <stdio.h>
+#include <cuda.h>
+#include <cutil.h>
+
+template <class T, class S>
+__global__ void subtractImage(T *output, const S *input, int N)
+{
+   int idx = blockIdx.x * blockDim.x + threadIdx.x;
+   if (idx<N) 
+   {
+      output[idx] -= input[idx];
+   }
+}
+
+float * SubtractImageKernelFunction(const float* input1, const float* input2, unsigned int N)
+{
+   float *output;
+
+   output = const_cast<float*>(input1);
+
+   // Compute execution configuration 
+   int blockSize = 128;
+   int nBlocks = N/blockSize + (N%blockSize == 0?0:1);
+
+   // Call kernel
+   subtractImage <<< nBlocks, blockSize >>> (output, input2, N);
+
+   // Return pointer to the output
+   return output;
+}

### 2011-04-18 Examples/Architecture1/src/SubtractImageFilter/CudaSubtractImageFilterKernel.h

@@ -1,0 +1,12 @@
+/*
+ * File Name:    cuda-kernel.h
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, January 18 2010, 10:00 
+ * Last Modified: Thursday, January 14 2010, 15:58
+ * 
+ * File Description:
+ *
+ */
+float * SubtractImageKernelFunction(const float* input1, const float* input2, unsigned int N);
+

### 2011-04-18 Examples/Architecture1/src/itk-gpu-multiply.cu

@@ -1,0 +1,105 @@
+/*
+ * File Name:    myFirstITKFilter.cxx
+ *
+ * Author:        Phillip Ward
+ * Creation Date: Monday, December 21 2009, 14:15 
+ * Last Modified: Friday, January 15 2010, 16:35
+ * 
+ * File Description:
+ *
+ */
+#include <stdio.h>
+#include <stdlib.h>
+
+#include "itkImage.h"
+#include "itkImageFileReader.h"
+#include "itkImageFileWriter.h"
+#include "CudaMultiplyImageFilter.h"
+#include "itkMultiplyImageFilter.h"
+#include "timer.h"
+
+using namespace std;
+
+int main(int argc, char **argv) {
+	double start, end;
+
+	// Pixel Types
+	typedef float InputPixelType;
+	typedef float OutputPixelType;
+	const unsigned int Dimension = 2;
+	int nFilters = atoi(argv[3]);
+
+	// IO Types
+	// typedef itk::RGBPixel< InputPixelType >       PixelType;
+	typedef itk::Image<InputPixelType, Dimension> InputImageType;
+	typedef itk::Image<OutputPixelType, Dimension> OutputImageType;
+	typedef itk::ImageFileReader<InputImageType> ReaderType;
+	typedef itk::ImageFileWriter<OutputImageType> WriterType;
+
+	typedef itk::CudaMultiplyImageFilter<InputImageType, OutputImageType> FilterType;
+
+	// Set Up Input File and Read Image
+	ReaderType::Pointer reader1 = ReaderType::New();
+	reader1->SetFileName(argv[1]);
+	ReaderType::Pointer reader2 = ReaderType::New();
+		reader2->SetFileName(argv[1]);
+
+	try {
+		reader1->Update();
+		reader2->Update();
+	} catch (itk::ExceptionObject exp) {
+		cerr << "Reader caused problem." << endl;
+		cerr << exp << endl;
+		return 1;
+	}
+
+	for (unsigned int i = 0; i < 3; ++i) {
+		if (i < Dimension) {
+			cout
+					<< reader1->GetOutput()->GetLargestPossibleRegion().GetSize()[i]
+					<< ", ";
+		} else {
+			cout << 1 << ", ";
+		}
+	}
+
+	FilterType::Pointer filter[nFilters];
+	filter[0] = FilterType::New();
+	filter[0]->SetInput(0,reader1->GetOutput());
[…]

### 2011-04-18 article/Article.tex
article template
Article update

--- 2011-03-01 trunk/article/Article.tex
@@
 % snail-mail address if you like.
-\author{Richard Beare}
-\authoraddress{Richard.Beare@med.monash.edu.au\\Department of Medicine\\Monash University\\Melbourne\\Australia}
+\author{Richard Beare{$^1$}, Daniel Micevski, Chris Share\\Luke Parkinson, Phillip Ward, Mike Kuiper{$^2$}}
+\authoraddress{{$^1$}Richard.Beare@monash.edu, Monash University, Melbourne, Australia\\
+{$^2$}mike@vpac.org, Victorian Partnership for Advanced Computing, Melbourne, Australia.}
 
@@
 \noindent
+There is great interest in the use of graphics processing units (GPU)
+for general purpose applications because the highly parallel
+architectures used in GPUs offer the potential for huge performance
+increases. The use of GPUs in image analysis applications has been
+under investigation for a number of years. This article describes
+modifications to the InsightToolkit (ITK) that provide a simple
+architecture for transparent use of GPU enabled filters and examples
+of how to write GPU enabled filters using the NVIDIA CUDA tools.
 \end{abstract}
@@
 \section{Introduction}
+Data must be resident in GPU device memory in order to be processed by
+the GPU. In order for an ITK filter to be accelerated using GPUs an
+image must be copied to the device memory and the result copied back
+if the next filter is not GPU enabled. Copying between host and device
+memory is quite slow and can easily offset any benefits achieved by
+faster GPU processing. It is therefore essential that redundant copies
+between host and device memory are eliminated. It is also desirable
+that new, GPU enabled, filters can be included in applications without
+changing programming style.
+
+This article describes a simple modification to the itk::Image class
+that allows transparent use of CUDA enabled filters. A range of
+standard filters have been implemented and extensive testing
+performed.
+
+\section{CITK Architecture}
+The aim of the architecture outline below was to allow GPU enabled
+filters to be included in an application without change of programming
+style or losing performance via redundant host to device memory copies.
+
+A number of architectures were considered. These were derived from online discussions and small samples of code available online:
+\begin{itemize}
+\item Break the pipeline at the beginning of filter execution by
+  copying data to device memory, processing, and then copying back
+  after execution completes. This isolates the GPU code from the rest
+  of the pipeline and requires no change to ITK infrastructure, but
+  introduces redundant copies if subsequent filters are GPU enabled.
+\item Include interface objects between filters in the pipeline to
+  manage copying. This can eliminate redundant copies but requires
+  that the programmer be aware of which filters are GPU enabled. There
+  is also a minor change of programming style.
+\end{itemize}
+
+Neither of these options require a modification to core ITK classes.
+
+The approach used in CITK does require a modification to core ITK
+classes, but has a number of advantages. The same approach has since
+been outlined on the ITK Wiki.
+
+The fundamental component of the pipeline is the ITK Image
+class. Within this class is a pixel container called {\em
+  ImportImageContainer}, used to manage the image data. CITK includes
+a substitute pixel container named {\em
+  CudaImportImageContainer}. This pixel container has all the same
+functionality of the {\em ImportImageContainer} which results in full
+compatibility with existing ITK components.
+
+The {\em CudaImportImageContainer} not only managed the image data on
+the host, but it also managed the image data on the device. When a
+standard filter requested the image data, such as through an iterator,
+the {\em CudaImportImageContainer} checks whether the most up to date
+image is on the device or the host. If it is on the device, it is
+copied back onto the host. This data is then supplied to the
+user. Similarly when a GPU filter requests the image data, the {\em
+  CudaImportImageContainer} would check where the most up to date
+image is, and copy it to the device if required.
+
+The {\em CudaImportImageContainer} can track where the most up to the
+date image is by which set command was used last, and assumes the data
+is modified when a standard iterator requests it.
+
+The result of this is memory transfers are only performed when
+required and are completed transparent to both the developer and the
+user. This leaves all the responsibility on the architect, rather than
+the developer or the user such as in the other attempts.
+
+\section{Anatomy of a CUDA enabled filter}
+\subsection{Image parameters}
+Different image operations require different image information. Number
+of pixels and image dimensions are all available in the normal way via
+GetSize, GetNumberOfPixels and related methods.
+
+\subsection{Memory management}
+
+Your CUDA kernel function should return a pointer to the output image as a global device pointer:
+
+{\tt typename TOutputImage::PixelType * ptr;}
+
+A pointer to input image memory is retrieved using:
+
+{\tt input->GetDevicePointer();}
+
+After the filter has completed, the output pointer must be given to
+the output image to be passed down the pipeline:
+
+{\tt output->GetPixelContainer()->SetDevicePointer(ptr, N, true);}
+
+In this example the {\tt ptr} is the pointer to output memory and the 'N'
+is the number of pixels in this image. The 'true' value is very
+important. This tells the output image to free the device memory once
+it is finished with it. WARNING: Setting this to false can lead to
+memory leaks on the device.
+
+\subsection{Templated kernel file}
+
+%\subsection{}
 
 \bibliographystyle{plain}
-\bibliography{local,InsightJournal}
+%\bibliography{local,InsightJournal}
+\bibliography{InsightJournal}
 \nocite{ITKSoftwareGuide}

### 2011-05-06 Examples/Architecture1/src/AbsImageFilter/CudaAbsImageFilterKernel.cu
tests and structural changes for voxel-wise operations completed

@@ -25,7 +25,7 @@ __global__ void AbsImageKernel(T *output, int N)
 }
 
 template <class T, class S>
-__global__ void AbsImageKernel(T *input, S *output, int N)
+__global__ void AbsImageKernel(S *output, const T *input, int N)
 {
    int idx = blockIdx.x * blockDim.x + threadIdx.x;
 
@@ -50,7 +50,7 @@ void AbsImageKernelFunction(const T * input, S * output, unsigned int N)
      }
    else
      {
-     AbsImageKernel<<< nBlocks, blockSize >>> (input, output, N);
+     AbsImageKernel<<< nBlocks, blockSize >>> (output, input, N);
      }
 
 }

### 2011-05-06 Examples/Architecture1/src/AddConstantToImageFilter/CudaAddConstantToImageFilterKernel.cu

@@ -12,8 +12,8 @@
 #include <cuda.h>
 #include <cutil.h>
 
-template <class T>
-__global__ void AddConstantToImageKernel(T *output, int N, T C)
+template <class S>
+__global__ void AddConstantToImageKernel(S *output, int N, S C)
 {
    int idx = blockIdx.x * blockDim.x + threadIdx.x;
    if (idx<N) 
@@ -22,20 +22,45 @@ __global__ void AddConstantToImageKernel(T *output, int N, T C)
    }
 }
 
-float * AddConstantToImageKernelFunction(const float* input, unsigned int N, float C)
+template <class T, class S>
+__global__ void AddConstantToImageKernel(S *output, const T *input, int N, T C)
 {
-   float *output;
+   int idx = blockIdx.x * blockDim.x + threadIdx.x;
+   if (idx<N) 
+   {
+      output[idx] = input[idx] + C;
+   }
+}
 
-   output = const_cast<float*>(input);
-
+template<class T, class S>
+void AddConstantToImageKernelFunction(const T* input, S* output, unsigned int N, T C)
+{
    // Compute execution configuration 
    int blockSize = 128;
    int nBlocks = N/blockSize + (N%blockSize == 0?0:1);
 
 
    // Call kernal
-   AddConstantToImageKernel <<< nBlocks, blockSize >>> (output, N, C);
+   if (output == input)
+     AddConstantToImageKernel <<< nBlocks, blockSize >>> (output, N, C);
+   else
+     AddConstantToImageKernel <<< nBlocks, blockSize >>> (output, input, N, C);
 
-   // Return pointer to the output
-   return output;
 }
+
+// versions we wish to compile
+#define THISTYPE float
+template void AddConstantToImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input, THISTYPE * output, unsigned int N, THISTYPE C);
+#undef THISTYPE
+#define THISTYPE int
+template void AddConstantToImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input, THISTYPE *output, unsigned int N, THISTYPE C);
+#undef THISTYPE
+
+#define THISTYPE short
+template void AddConstantToImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input, THISTYPE *output, unsigned int N, THISTYPE C);
+#undef THISTYPE
+
+#define THISTYPE char
[…]

### 2011-05-06 Examples/Architecture1/src/AddConstantToImageFilter/CudaAddConstantToImageFilterKernel.h

@@ -8,5 +8,6 @@
  * File Description:
  *
  */
-float * AddConstantToImageKernelFunction(const float* input1, unsigned int N, float C);
+template <class T, class S> extern
+void AddConstantToImageKernelFunction(const T* input1, S* output, unsigned int N, T C);
 

### 2011-05-06 Examples/Architecture1/src/BinaryThresholdImageFilter/CudaBinaryThresholdImageFilter.h

@@ -25,7 +25,7 @@ SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
 #ifndef __CudaBinaryThresholdImageFilter_h
 #define __CudaBinaryThresholdImageFilter_h
 
-#include "itkImageToImageFilter.h"
+#include "CudaInPlaceImageFilter.h"
 
 namespace itk
 {
@@ -63,14 +63,14 @@ namespace itk
  *
  * \ingroup IntensityImageFilters  CudaEnabled
  *
- * \sa ImageToImageFilter
+ * \sa CudaInPlaceImageFilter
  */
 
 
    template <class TInputImage, class TOutputImage>
       class ITK_EXPORT CudaBinaryThresholdImageFilter :
          public
-         ImageToImageFilter<TInputImage, TOutputImage >
+         CudaInPlaceImageFilter<TInputImage, TOutputImage >
    {
       public:
 
@@ -79,14 +79,14 @@ namespace itk
 
 
          typedef CudaBinaryThresholdImageFilter           Self;
-         typedef ImageToImageFilter<TInputImage,TOutputImage > 
+         typedef CudaInPlaceImageFilter<TInputImage,TOutputImage >
                                              Superclass;
          typedef SmartPointer<Self>          Pointer;
          typedef SmartPointer<const Self>    ConstPointer;
 
          itkNewMacro(Self);
 
-         itkTypeMacro(CudaBinaryThresholdImageFilter, ImageToImageFilter);
+         itkTypeMacro(CudaBinaryThresholdImageFilter, CudaInPlaceImageFilter);
 
          typedef typename InputImageType::PixelType   InputPixelType;
          typedef typename OutputImageType::PixelType  OutputPixelType;

### 2011-05-06 Examples/Architecture1/src/BinaryThresholdImageFilter/CudaBinaryThresholdImageFilterKernel.cu

@@ -12,36 +12,74 @@
 #include <cuda.h>
 #include <cutil.h>
 
-template <class T>
-__global__ void binaryThreshold(T *output, T lower, T upper, T inside, T outside, int N)
+template <class T, class S>
+__global__ void binaryThreshold(S *output, T lower, T upper, S inside, S outside, int N)
 {
    int idx = blockIdx.x * blockDim.x + threadIdx.x;
    if (idx<N) 
    {
-      float i = output[idx];
-      if (i>upper || i<lower)
+      T A = output[idx];
+      if ( lower <= A && A <= upper )
       {
-         output[idx] = inside;
+      output[idx] = inside;
       }
       else
-      {
-         output[idx] = outside;
-      }
+	{
+	output[idx] = outside;
+	}
    }
 }
 
-float * BinaryThreshold(const float* input, float m_LowerThreshold, float m_UpperThreshold, float m_InsideValue, float m_OutsideValue, unsigned int N)
+template <class T, class S>
+__global__ void binaryThreshold(S *output, const T *input, T lower, T upper, S inside, S outside, int N)
 {
-   // pointers
-   //float *output;
-   float *output = const_cast<float*>(input);
+   int idx = blockIdx.x * blockDim.x + threadIdx.x;
+   if (idx<N) 
+   {
+      T A = input[idx];
+      if ( lower <= A && A <= upper )
+      {
+      output[idx] = inside;
+      }
+      else
+	{
+	output[idx] = outside;
+	}
+   }
+}
 
+template <class T, class S> 
+void BinaryThresholdImageKernelFunction(const T* input, S* output, T m_LowerThreshold,
+T m_UpperThreshold, S m_InsideValue, S m_OutsideValue, unsigned int N)
+{
    // Compute execution configuration
    int blockSize = 128;
    int nBlocks = N/blockSize + (N%blockSize == 0?0:1);
-
    // Call  kernel
-   binaryThreshold <<< nBlocks, blockSize >>> (output, m_LowerThreshold, m_UpperThreshold, m_InsideValue, m_OutsideValue, N);
+   if (output == input)
+     binaryThreshold <<< nBlocks, blockSize >>> (output, m_LowerThreshold, m_UpperThreshold, m_InsideValue, m_OutsideValue, N);
+   else
[…]

### 2011-05-06 Examples/Architecture1/src/DivideByConstantImageFilter/CudaDivideByConstantImageFilterKernel.cu

@@ -12,30 +12,57 @@
 #include <cuda.h>
 #include <cutil.h>
 
-template <class T>
-__global__ void DivideByConstantImageKernel(T *output, int N, T C)
+template <class S>
+__global__ void DivideByConstantImageKernel(S *output, int N, S C)
 {
    int idx = blockIdx.x * blockDim.x + threadIdx.x;
    if (idx<N) 
    {
-      output[idx] = output[idx] / C;
-      
+      output[idx] /= C;
    }
 }
 
-float * DivideByConstantImageKernelFunction(const float* input1, unsigned int N, float C)
+template <class T, class S>
+__global__ void DivideByConstantImageKernel(S *output, const T *input, int N, T C)
 {
-   float *output;
+   int idx = blockIdx.x * blockDim.x + threadIdx.x;
+   if (idx<N) 
+   {
+      output[idx] = input[idx] / C;
+   }
+}
 
-   output = const_cast<float*>(input1);
-
+template<class T, class S>
+void DivideByConstantImageKernelFunction(const T* input, S* output, unsigned int N, T C)
+{
    // Compute execution configuration 
    int blockSize = 128;
    int nBlocks = N/blockSize + (N%blockSize == 0?0:1);
 
-   // Call kernal
-   DivideByConstantImageKernel <<< nBlocks, blockSize >>> (output, N, C);
 
-   // Return pointer to the output
-   return output;
+   // Call kernal
+   if (output == input)
+     DivideByConstantImageKernel <<< nBlocks, blockSize >>> (output, N, C);
+   else
+     DivideByConstantImageKernel <<< nBlocks, blockSize >>> (output, input, N, C);
+
 }
+// versions we wish to compile
+#define THISTYPE float
+template void DivideByConstantImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input, THISTYPE
+ * output, unsigned int N, THISTYPE C);
+#undef THISTYPE
+#define THISTYPE int
+template void DivideByConstantImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input, THISTYPE
+ *output, unsigned int N, THISTYPE C);
+#undef THISTYPE
+
+#define THISTYPE short
+template void DivideByConstantImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input, THISTYPE
+ *output, unsigned int N, THISTYPE C);
+#undef THISTYPE
+
[…]

### 2011-05-06 Examples/Architecture1/src/DivideImageFilter/CudaDivideImageFilter.h

@@ -26,7 +26,7 @@ SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
 #ifndef __itkCudaDivideImageFilter_h
 #define __itkCudaDivideImageFilter_h
 
-#include "itkImageToImageFilter.h"
+#include "CudaInPlaceImageFilter.h"
 
 namespace itk
 {
@@ -43,14 +43,14 @@ namespace itk
  *
  * \ingroup IntensityImageFilters  CudaEnabled
  * 
- * \sa ImageToImageFilter
+ * \sa CudaInPlaceImageFilter
  */
 
 
 template <class TInputImage, class TOutputImage>
 class ITK_EXPORT CudaDivideImageFilter :
     public
-ImageToImageFilter<TInputImage, TOutputImage >
+CudaInPlaceImageFilter<TInputImage, TOutputImage >
 {
 public:
 
@@ -59,7 +59,7 @@ public:
 
   /** Standard class typedefs. */
   typedef CudaDivideImageFilter  Self;
-  typedef ImageToImageFilter<TInputImage,TOutputImage >
+  typedef CudaInPlaceImageFilter<TInputImage,TOutputImage >
                                              Superclass;
   typedef SmartPointer<Self>        Pointer;
   typedef SmartPointer<const Self>  ConstPointer;
@@ -69,7 +69,7 @@ public:
 
   /** Runtime information support. */
   itkTypeMacro(CudaDivideImageFilter,
-               ImageToImageFilter);
+               CudaInPlaceImageFilter);
 
   typedef typename InputImageType::PixelType   InputPixelType;
   typedef typename OutputImageType::PixelType  OutputPixelType;

### 2011-05-06 Examples/Architecture1/src/MaximumImageFilter/CudaMaximumImageFilter.h

@@ -26,7 +26,7 @@ SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
 #ifndef __itkCudaMaximumImageFilter_h
 #define __itkCudaMaximumImageFilter_h
 
-#include "itkImageToImageFilter.h"
+#include "CudaInPlaceImageFilter.h"
 
 namespace itk
 {
@@ -45,14 +45,14 @@ namespace itk
  *
  * \ingroup IntensityImageFilters  CudaEnabled
  * 
- * \sa ImageToImageFilter
+ * \sa CudaInPlaceImageFilter
  */
 
 
 template <class TInputImage, class TOutputImage>
 class ITK_EXPORT CudaMaximumImageFilter :
     public
-ImageToImageFilter<TInputImage, TOutputImage >
+CudaInPlaceImageFilter<TInputImage, TOutputImage >
 {
 public:
 
@@ -61,7 +61,7 @@ public:
 
   /** Standard class typedefs. */
   typedef CudaMaximumImageFilter  Self;
-  typedef ImageToImageFilter<TInputImage,TOutputImage >
+  typedef CudaInPlaceImageFilter<TInputImage,TOutputImage >
                                              Superclass;
   typedef SmartPointer<Self>        Pointer;
   typedef SmartPointer<const Self>  ConstPointer;
@@ -71,7 +71,7 @@ public:
 
   /** Runtime information support. */
   itkTypeMacro(CudaMaximumImageFilter,
-               ImageToImageFilter);
+               CudaInPlaceImageFilter);
 
   typedef typename InputImageType::PixelType   InputPixelType;
   typedef typename OutputImageType::PixelType  OutputPixelType;

### 2011-05-06 Examples/Architecture1/src/MaximumImageFilter/CudaMaximumImageFilterKernel.cu

@@ -1,7 +1,7 @@
 /*
  * File Name:    cuda-kernel.cu
  *
- * Author:        Phillip Ward
+ * Author:        Phillip Ward, Richard Beare
  * Creation Date: Monday, January 18 2010, 10:00 
  * Last Modified: Wednesday, December 23 2009, 16:35 
  * 
@@ -13,7 +13,7 @@
 #include <cutil.h>
 
 template <class T, class S>
-__global__ void MaximumImageKernel(T *output, const S *input, int N)
+__global__ void MaximumImageKernel(S *output, const T *input, int N)
 {
    int idx = blockIdx.x * blockDim.x + threadIdx.x;
    if (idx<N) 
@@ -26,19 +26,47 @@ __global__ void MaximumImageKernel(T *output, const S *input, int N)
    }
 }
 
-float * MaximumImageKernelFunction(const float* input1, const float* input2, unsigned int N)
+template <class T, class S>
+__global__ void MaximumImageKernel(S *output, const T *input1, const T* input2, int N)
 {
-   float *output;
+   int idx = blockIdx.x * blockDim.x + threadIdx.x;
+   if (idx<N) 
+   {
+   T in1 = input1[idx];
+   T in2 = input2[idx]; 
+   output[idx] = (in1>in2)?in1:in2;
+   }
+}
 
-   output = const_cast<float*>(input1);
-
+template <class T, class S>
+void MaximumImageKernelFunction(const T* input1, const T* input2, S* output, unsigned int N)
+{
    // Compute execution configuration 
    int blockSize = 128;
    int nBlocks = N/blockSize + (N%blockSize == 0?0:1);
 
    // Call kernal
-   MaximumImageKernel <<< nBlocks, blockSize >>> (output, input2, N);
+   if (output == input1)
+     MaximumImageKernel <<< nBlocks, blockSize >>> (output, input2, N);
+   else
+     MaximumImageKernel <<< nBlocks, blockSize >>> (output, input1, input2, N);
 
    // Return pointer to the output
-   return output;
 }
+
+// versions we wish to compile
+#define THISTYPE float
+template void MaximumImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, const THISTYPE * input2, THISTYPE * output, unsigned int N);
+#undef THISTYPE
+#define THISTYPE int
[…]

### 2011-05-06 Examples/Architecture1/src/MultiplyByConstantImageFilter/CudaMultiplyByConstantImageFilterKernel.cu

@@ -12,29 +12,54 @@
 #include <cuda.h>
 #include <cutil.h>
 
-#include "CudaMultiplyByConstantImageFilterKernel.h"
 
-template <class T>
-__global__ void MultiplyByConstantImageKernel(T *output, int N, T C) {
-	int idx = blockIdx.x * blockDim.x + threadIdx.x;
-	if (idx < N) {
-		output[idx] *= C;
-	}
+template <class S>
+__global__ void MultiplyByConstantImageKernel(S *output, int N, S C)
+{
+   int idx = blockIdx.x * blockDim.x + threadIdx.x;
+   if (idx<N) 
+   {
+      output[idx] *= C;
+   }
 }
 
-CITK_OUT * MultiplyByConstantImageKernelFunction(const CIT_IN1* input1,
-		unsigned int N, CITK_IN1 C) {
-	CITK_OUT *output;
-
-	output = const_cast<CITK_IN1*> (input1);
-
-	// Compute execution configuration
-	int blockSize = 128;
-	int nBlocks = N / blockSize + (N % blockSize == 0 ? 0 : 1);
-
-	// Call kernel
-	MultiplyByConstantImageKernel <<< nBlocks, blockSize >>> (output, N, C);
-
-	// Return pointer to the output
-	return output;
+template <class T, class S>
+__global__ void MultiplyByConstantImageKernel(S *output, const T *input, int N, T C)
+{
+   int idx = blockIdx.x * blockDim.x + threadIdx.x;
+   if (idx<N) 
+   {
+      output[idx] = input[idx] * C;
+   }
 }
+
+template<class T, class S>
+void MultiplyByConstantImageKernelFunction(const T* input, S* output, unsigned int N, T C)
+{
+   // Compute execution configuration 
+   int blockSize = 128;
+   int nBlocks = N/blockSize + (N%blockSize == 0?0:1);
+
+
+   // Call kernal
+   if (output == input)
+     MultiplyByConstantImageKernel <<< nBlocks, blockSize >>> (output, N, C);
+   else
+     MultiplyByConstantImageKernel <<< nBlocks, blockSize >>> (output, input, N, C);
+
+}
+// versions we wish to compile
+#define THISTYPE float
+template void MultiplyByConstantImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input, THISTYPE * output, unsigned int N, THISTYPE C);
+#undef THISTYPE
+#define THISTYPE int
[…]

### 2011-05-06 Examples/Architecture1/src/MultiplyByConstantImageFilter/CudaMultiplyByConstantImageFilterKernel.h

@@ -9,5 +9,5 @@
  *
  */
 
-CITK_OUT * MultiplyByConstantImageKernelFunction(const CITK_IN1 * input1, unsigned int N, CITK_IN1 C);
-
+template <class T, class S> extern
+void MultiplyByConstantImageKernelFunction(const T* input1, S* output, unsigned int N, T C);

### 2011-05-06 Examples/Architecture1/src/MultiplyImageFilter2/CudaMultiplyImageFilterKernel.cu

@@ -13,7 +13,7 @@
 #include <cutil.h>
 
 template <class T, class S>
-__global__ void multiplyImage(T *output, const S *input, int N)
+__global__ void multiplyImage(S *output, const T *input, int N)
 {
    int idx = blockIdx.x * blockDim.x + threadIdx.x;
    if (idx<N) 
@@ -23,7 +23,7 @@ __global__ void multiplyImage(T *output, const S *input, int N)
 }
 
 template <class T, class S>
-__global__ void multiplyImage2(T *output, const S *input1, const S *input2, int N)
+__global__ void multiplyImage(S *output, const T *input1, const T *input2, int N)
 {
    int idx = blockIdx.x * blockDim.x + threadIdx.x;
    if (idx<N) 
@@ -36,10 +36,7 @@ __global__ void multiplyImage2(T *output, const S *input1, const S *input2, int 
 template <class T, class S>
 void MultiplyImageKernelFunction(const T* input1, const T* input2, S *output, unsigned int N)
 {
-//   S *output;
-
-//   output = const_cast<S*>(input1);
-
+  
    // Compute execution configuration 
    int blockSize = 128;
    int nBlocks = N/blockSize + (N%blockSize == 0?0:1);
@@ -48,29 +45,29 @@ void MultiplyImageKernelFunction(const T* input1, const T* input2, S *output, un
    if (output == input1)
      multiplyImage <<< nBlocks, blockSize >>> (output, input2, N);
    else
-     multiplyImage2 <<< nBlocks, blockSize >>> (output, input1, input2, N);
+     multiplyImage <<< nBlocks, blockSize >>> (output, input1, input2, N);
      
    // Return pointer to the output
    //return output;
 }
 
 
-template void MultiplyImageKernelFunction<float, float>(const float *input1, const float *input2,  float *output, unsigned int N);
+//template void MultiplyImageKernelFunction<float, float>(const float *input1, const float *input2,  float *output, unsigned int N);
 
-#if 0
+
 // versions we wish to compile
 #define THISTYPE float
-template void MultiplyImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, const THISTYPE * input2, const THISTYPE * output, unsigned int N);
[…]

### 2011-05-06 Examples/Architecture1/src/SubtractImageFilter/CudaSubtractImageFilterKernel.cu

@@ -13,7 +13,7 @@
 #include <cutil.h>
 
 template <class T, class S>
-__global__ void subtractImage(T *output, const S *input, int N)
+__global__ void subtractImage(S *output, const T *input, int N)
 {
    int idx = blockIdx.x * blockDim.x + threadIdx.x;
    if (idx<N) 
@@ -22,19 +22,44 @@ __global__ void subtractImage(T *output, const S *input, int N)
    }
 }
 
-float * SubtractImageKernelFunction(const float* input1, const float* input2, unsigned int N)
+template <class T, class S>
+__global__ void subtractImage(S *output, const T *input1, const T *input2, int N)
 {
-   float *output;
+   int idx = blockIdx.x * blockDim.x + threadIdx.x;
+   if (idx<N) 
+   {
+      output[idx] = input1[idx] - input2[idx];
+   }
+}
 
-   output = const_cast<float*>(input1);
-
-   // Compute execution configuration 
+template <class T, class S>
+void SubtractImageKernelFunction(const T* input1, const T* input2, S *output, unsigned int N)
+{
+  // Compute execution configuration 
    int blockSize = 128;
    int nBlocks = N/blockSize + (N%blockSize == 0?0:1);
 
    // Call kernel
-   subtractImage <<< nBlocks, blockSize >>> (output, input2, N);
+   if (output == input1)
+     subtractImage <<< nBlocks, blockSize >>> (output, input2, N);
+   else
+     subtractImage <<< nBlocks, blockSize >>> (output, input1, input2, N);
 
-   // Return pointer to the output
-   return output;
 }
+
+// versions we wish to compile
+#define THISTYPE float
+template void SubtractImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, const THISTYPE * input2, THISTYPE * output, unsigned int N);
+#undef THISTYPE
+#define THISTYPE int
+template void SubtractImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, const THISTYPE * input2, THISTYPE *output, unsigned int N);
+#undef THISTYPE
+
+#define THISTYPE short
+template void SubtractImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, const THISTYPE * input2, THISTYPE *output, unsigned int N);
+#undef THISTYPE
+
+#define THISTYPE char
[…]

### 2011-05-06 Examples/Architecture1/src/SubtractImageFilter/CudaSubtractImageFilterKernel.h

@@ -8,5 +8,8 @@
  * File Description:
  *
  */
-float * SubtractImageKernelFunction(const float* input1, const float* input2, unsigned int N);
+template <class T, class S> extern
+void SubtractImageKernelFunction(const T* input1, const T* input2, S* output, unsigned int N);
+
+
 

### 2011-05-06 trunk/Examples/Architecture1/src/AbsImageFilter/CudaAbsImageFilter.h
tests and structural changes for voxel-wise operations completed

@@ -30,10 +30,10 @@ SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
 
 namespace itk
 {
-  
+
 /** \class CudaAbsImageFilter
  * \brief Computes the ABS(x) pixel-wise
- * 
+ *
  * \author Phillip Ward, Victorian Partnership for Advanced Computing (VPAC)
  *         Richard Beare, Monash University.
  * \ingroup IntensityImageFilters  CudaEnabled
@@ -61,7 +61,7 @@ public:
   itkNewMacro(Self);
 
   /** Runtime information support. */
-  itkTypeMacro(CudaAbsImageFilter, 
+  itkTypeMacro(CudaAbsImageFilter,
                ImageToImageFilter);
 
   typedef typename InputImageType::PixelType   InputPixelType;

### 2011-05-06 trunk/Examples/Architecture1/src/AddConstantToImageFilter/CudaAddConstantToImageFilter.h

@@ -26,7 +26,7 @@ SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
 #ifndef __itkCudaAddConstantToImageFilter_h
 #define __itkCudaAddConstantToImageFilter_h
 
-#include "itkImageToImageFilter.h"
+#include "CudaInPlaceImageFilter.h"
 
 namespace itk
 {
@@ -49,7 +49,7 @@ namespace itk
 template <class TInputImage, class TOutputImage>
 class ITK_EXPORT CudaAddConstantToImageFilter :
     public
-ImageToImageFilter<TInputImage, TOutputImage >
+CudaInPlaceImageFilter<TInputImage, TOutputImage >
 {
 public:
 
@@ -58,7 +58,7 @@ public:
 
   /** Standard class typedefs. */
   typedef CudaAddConstantToImageFilter  Self;
-  typedef ImageToImageFilter<TInputImage,TOutputImage >
+  typedef CudaInPlaceImageFilter<TInputImage,TOutputImage >
                                              Superclass;
   typedef SmartPointer<Self>        Pointer;
   typedef SmartPointer<const Self>  ConstPointer;
@@ -68,7 +68,7 @@ public:
 
   /** Runtime information support. */
   itkTypeMacro(CudaAddConstantToImageFilter,
-               ImageToImageFilter);
+               CudaInPlaceImageFilter);
 
   typedef typename InputImageType::PixelType   InputPixelType;
   typedef typename OutputImageType::PixelType  OutputPixelType;
@@ -94,7 +94,7 @@ public:
                    typename TOutputImage::PixelType>));
   itkConceptMacro(Input1Input2OutputAddOperatorCheck,
                   (Concept::AdditiveOperators<typename TInputImage::PixelType,
-                   TConstant,
+                   InputPixelType, 
                    typename TOutputImage::PixelType>));
   /** End concept checking */
 #endif

### 2011-05-06 trunk/Examples/Architecture1/src/AddImageFilter/CudaAddImageFilter.h

@@ -26,7 +26,7 @@ SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
 #ifndef __itkCudaAddImageFilter_h
 #define __itkCudaAddImageFilter_h
 
-#include "itkImageToImageFilter.h"
+#include "CudaInPlaceImageFilter.h"
 
 namespace itk
 {
@@ -65,14 +65,14 @@ namespace itk
  *
  * \ingroup IntensityImageFilters  CudaEnabled
  * 
- * \sa ImageToImageFilter
+ * \sa CudaInPlaceImageFilter
  */
 
 
 template <class TInputImage, class TOutputImage>
 class ITK_EXPORT CudaAddImageFilter :
     public
-ImageToImageFilter<TInputImage, TOutputImage >
+CudaInPlaceImageFilter<TInputImage, TOutputImage >
 {
 public:
 
@@ -81,7 +81,7 @@ public:
 
   /** Standard class typedefs. */
   typedef CudaAddImageFilter  Self;
-  typedef ImageToImageFilter<TInputImage,TOutputImage >
+  typedef CudaInPlaceImageFilter<TInputImage,TOutputImage >
                                              Superclass;
   typedef SmartPointer<Self>        Pointer;
   typedef SmartPointer<const Self>  ConstPointer;
@@ -91,7 +91,7 @@ public:
 
   /** Runtime information support. */
   itkTypeMacro(CudaAddImageFilter,
-               ImageToImageFilter);
+               CudaInPlaceImageFilter);
 
   typedef typename InputImageType::PixelType   InputPixelType;
   typedef typename OutputImageType::PixelType  OutputPixelType;

### 2011-05-06 trunk/Examples/Architecture1/src/AddImageFilter/CudaAddImageFilterKernel.cu

@@ -22,19 +22,44 @@ __global__ void AddImageKernel(T *output, const S *input, int N)
    }
 }
 
-float * AddImageKernelFunction(const float* input1, const float* input2, unsigned int N)
+template <class T, class S>
+__global__ void AddImageKernel(T *output, const S *input1, const S* input2, int N)
 {
-   float *output;
+   int idx = blockIdx.x * blockDim.x + threadIdx.x;
+   if (idx<N) 
+   {
+      output[idx] = input1[idx] + input2[idx];
+   }
+}
 
-   output = const_cast<float*>(input1);
+template <class T, class S>
+void AddImageKernelFunction(const T* input1, const T* input2, S* output, unsigned int N)
+{
+
 
    // Compute execution configuration 
    int blockSize = 128;
    int nBlocks = N/blockSize + (N%blockSize == 0?0:1);
 
    // Call kernal
-   AddImageKernel <<< nBlocks, blockSize >>> (output, input2, N);
-
-   // Return pointer to the output
-   return output;
+   if (output == input1)
+     AddImageKernel <<< nBlocks, blockSize >>> (output, input2, N);
+   else
+     AddImageKernel <<< nBlocks, blockSize >>> (output, input1, input2, N);
 }
+
+// versions we wish to compile
+#define THISTYPE float
+template void AddImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, const THISTYPE * input2, THISTYPE * output, unsigned int N);
+#undef THISTYPE
+#define THISTYPE int
+template void AddImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, const THISTYPE * input2, THISTYPE *output, unsigned int N);
+#undef THISTYPE
+
+#define THISTYPE short
+template void AddImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, const THISTYPE * input2, THISTYPE *output, unsigned int N);
+#undef THISTYPE
+
+#define THISTYPE char
+template void AddImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, const THISTYPE * input2,  THISTYPE *output, unsigned int N);
+#undef THISTYPE

### 2011-05-06 trunk/Examples/Architecture1/src/AddImageFilter/CudaAddImageFilterKernel.h

@@ -8,5 +8,6 @@
  * File Description:
  *
  */
-float * AddImageKernelFunction(const float* input1, const float* input2, unsigned int N);
+template <class T, class S> extern
+void AddImageKernelFunction(const T* input1, const T* input2, S* output, unsigned int N);
 

### 2011-05-06 trunk/Examples/Architecture1/src/BinaryThresholdImageFilter/CudaBinaryThresholdImageFilterKernel.h

@@ -1,17 +1,6 @@
-/*
- * File Name:    cuda-kernel.h
- *
- * Author:        Phillip Ward
- * Creation Date: Wednesday, December 23 2009, 16:59 
- * Last Modified: Friday, January 15 2010, 15:18
- * 
- * File Description:
- *
- */
-//__global__ void binaryThreshold(float *output,
-//float lower, float upper, float inside, float outside, int N);
 
-float* BinaryThreshold(const float* input, float m_LowerThreshold,
-float m_UpperThreshold, float m_InsideValue, float m_OutsideValue,
+template <class T, class S> extern
+void BinaryThresholdImageKernelFunction(const T* input, S* output, T m_LowerThreshold,
+T m_UpperThreshold, S m_InsideValue, S m_OutsideValue,
 unsigned int N);
 

### 2011-05-06 trunk/Examples/Architecture1/src/DivideByConstantImageFilter/CudaDivideByConstantImageFilter.h

@@ -26,7 +26,7 @@ SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
 #ifndef __itkCudaDivideByConstantImageFilter_h
 #define __itkCudaDivideByConstantImageFilter_h
 
-#include "itkImageToImageFilter.h"
+#include "CudaInPlaceImageFilter.h"
 
 namespace itk
 {
@@ -41,12 +41,12 @@ namespace itk
  * \author Phillip Ward, Victorian Partnership for Advanced Computing (VPAC)
  *
  * \ingroup IntensityImageFilters  CudaEnabled
- * \sa ImageToImageFilter
+ * \sa CudaInPlaceImageFilter
  */
 template <class TInputImage, class TOutputImage>
 class ITK_EXPORT CudaDivideByConstantImageFilter :
     public
-ImageToImageFilter<TInputImage, TOutputImage >
+CudaInPlaceImageFilter<TInputImage, TOutputImage >
 {
 public:
 
@@ -55,7 +55,7 @@ public:
 
   /** Standard class typedefs. */
   typedef CudaDivideByConstantImageFilter  Self;
-  typedef ImageToImageFilter<TInputImage,TOutputImage >
+  typedef CudaInPlaceImageFilter<TInputImage,TOutputImage >
                                              Superclass;
   typedef SmartPointer<Self>        Pointer;
   typedef SmartPointer<const Self>  ConstPointer;
@@ -65,7 +65,7 @@ public:
 
   /** Runtime information support. */
   itkTypeMacro(CudaDivideByConstantImageFilter,
-               ImageToImageFilter);
+               CudaInPlaceImageFilter);
 
   typedef typename InputImageType::PixelType   InputPixelType;
   typedef typename OutputImageType::PixelType  OutputPixelType;
@@ -83,11 +83,15 @@ public:
   {
 	  return m_Constant;
   }
-
+#ifdef ITK_USE_CONCEPT_CHECKING
   /** Begin concept checking */
   itkConceptMacro(InputConvertibleToOutputCheck,
                    (Concept::Convertible<typename TInputImage::PixelType,
                     typename TOutputImage::PixelType>));
+  itkConceptMacro(Input1Input2OutputDivideOperatorCheck,
+                  (Concept::DivisionOperators<typename TInputImage::PixelType,
+                   InputPixelType, 
+                   typename TOutputImage::PixelType>));
   /** End concept checking */
 #endif
 

### 2011-05-06 trunk/Examples/Architecture1/src/DivideByConstantImageFilter/CudaDivideByConstantImageFilterKernel.h

@@ -8,5 +8,6 @@
  * File Description:
  *
  */
-float * DivideByConstantImageKernelFunction(const float* input1, unsigned int N, float C);
+template <class T, class S> extern
+void DivideByConstantImageKernelFunction(const T* input1, S* output, unsigned int N, T C);
 

### 2011-05-06 trunk/Examples/Architecture1/src/DivideImageFilter/CudaDivideImageFilterKernel.cu

@@ -13,7 +13,7 @@
 #include <cutil.h>
 
 template <class T, class S>
-__global__ void DivideImageKernel(T *output, const S *input, int N, T MAX)
+__global__ void DivideImageKernel(S *output, const T *input, int N, S MAX)
 {
    int idx = blockIdx.x * blockDim.x + threadIdx.x;
    if (idx<N) 
@@ -23,20 +23,45 @@ __global__ void DivideImageKernel(T *output, const S *input, int N, T MAX)
    }
 }
 
-float * DivideImageKernelFunction(const float* input1, const float* input2, unsigned int N, float MAX)
+template <class T, class S>
+__global__ void DivideImageKernel(S *output, const T *input1, const T *input2, int N, S MAX)
 {
-   float *output;
+   int idx = blockIdx.x * blockDim.x + threadIdx.x;
+   if (idx<N) 
+   {
+      output[idx] = output[idx] / input1[idx];
+      if (input1[idx]==0) { output[idx] = MAX; }
+   }
+}
 
-   output = const_cast<float*>(input1);
-
+template <class T, class S>
+void DivideImageKernelFunction(const T* input1, const T* input2, S *output, unsigned int N, S MAX)
+{
    // Compute execution configuration 
    int blockSize = 64;
    int nBlocks = N/blockSize + (N%blockSize == 0?0:1);
 
 
    // Call kernal
-   DivideImageKernel <<< nBlocks, blockSize >>> (output, input2, N, MAX);
-
-   // Return pointer to the output
-   return output;
+   if (output == input1)
+     DivideImageKernel <<< nBlocks, blockSize >>> (output, input2, N, MAX);
+   else
+     DivideImageKernel <<< nBlocks, blockSize >>> (output, input1, input2, N, MAX);
 }
+
+// versions we wish to compile
+#define THISTYPE float
+template void DivideImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, const THISTYPE * input2, THISTYPE * output, unsigned int N, THISTYPE MAX);
+#undef THISTYPE
+#define THISTYPE int
+template void DivideImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, const THISTYPE * input2, THISTYPE *output, unsigned int N, THISTYPE MAX);
+#undef THISTYPE
+
+#define THISTYPE short
[…]

### 2011-05-06 trunk/Examples/Architecture1/src/DivideImageFilter/CudaDivideImageFilterKernel.h

@@ -8,5 +8,6 @@
  * File Description:
  *
  */
-float * DivideImageKernelFunction(const float* input1, const float* input2, unsigned int N, float MAX);
+template <class T, class S> extern
+void DivideImageKernelFunction(const T* input1, const T* input2, S* output, unsigned int N, S MAX);
 

### 2011-05-06 trunk/Examples/Architecture1/src/MaximumImageFilter/CudaMaximumImageFilterKernel.h

@@ -1,12 +1,3 @@
-/*
- * File Name:    cuda-kernel.h
- *
- * Author:        Phillip Ward
- * Creation Date: Monday, January 18 2010, 10:00 
- * Last Modified: Thursday, January 14 2010, 15:58
- * 
- * File Description:
- *
- */
-float * MaximumImageKernelFunction(const float* input1, const float* input2, unsigned int N);
+template <class T, class S> extern
+void MaximumImageKernelFunction(const T* input1, const T* input2, S* output, unsigned int N);
 

### 2011-05-06 trunk/Examples/Architecture1/src/MultiplyByConstantImageFilter/CudaMultiplyByConstantImageFilter.h

@@ -26,7 +26,7 @@ SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
 #ifndef __itkCudaMultiplyByConstantImageFilter_h
 #define __itkCudaMultiplyByConstantImageFilter_h
 
-#include "itkImageToImageFilter.h"
+#include "CudaInPlaceImageFilter.h"
 
 namespace itk
 {
@@ -42,14 +42,14 @@ namespace itk
  *
  * \ingroup IntensityImageFilters  CudaEnabled
  *
- * \sa ImageToImageFilter
+ * \sa CudaInPlaceImageFilter
  */
 
 
 template <class TInputImage, class TOutputImage>
 class ITK_EXPORT CudaMultiplyByConstantImageFilter :
     public
-ImageToImageFilter<TInputImage, TOutputImage >
+CudaInPlaceImageFilter<TInputImage, TOutputImage >
 {
 public:
 
@@ -58,7 +58,7 @@ public:
 
   /** Standard class typedefs. */
   typedef CudaMultiplyByConstantImageFilter  Self;
-  typedef ImageToImageFilter<TInputImage,TOutputImage >
+  typedef CudaInPlaceImageFilter<TInputImage,TOutputImage >
                                              Superclass;
   typedef SmartPointer<Self>        Pointer;
   typedef SmartPointer<const Self>  ConstPointer;
@@ -68,7 +68,7 @@ public:
 
   /** Runtime information support. */
   itkTypeMacro(CudaMultiplyByConstantImageFilter,
-               ImageToImageFilter);
+               CudaInPlaceImageFilter);
 
   typedef typename InputImageType::PixelType   InputPixelType;
   typedef typename OutputImageType::PixelType  OutputPixelType;
@@ -94,7 +94,7 @@ public:
                    typename TOutputImage::PixelType>));
   itkConceptMacro(Input1Input2OutputMultiplyOperatorCheck,
                   (Concept::MultiplyOperator<typename TInputImage::PixelType,
-                   TConstant,
+                   InputPixelType,
                    typename TOutputImage::PixelType>));
   /** End concept checking */
 #endif

### 2011-05-06 trunk/Examples/Architecture1/src/SubtractConstantFromImageFilter/CudaSubtractConstantFromImageFilter.h

@@ -26,7 +26,7 @@ SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
 #ifndef __itkCudaSubtractConstantFromImageFilter_h
 #define __itkCudaSubtractConstantFromImageFilter_h
 
-#include "itkImageToImageFilter.h"
+#include "CudaInPlaceImageFilter.h"
 
 namespace itk
 {
@@ -42,13 +42,13 @@ namespace itk
  *
  * \ingroup IntensityImageFilters CudaEnabled
  *
- * \sa ImageToImageFilter
+ * \sa CudaImageToImageFilter
  */
 
 template <class TInputImage, class TOutputImage>
 class ITK_EXPORT CudaSubtractConstantFromImageFilter :
     public
-ImageToImageFilter<TInputImage, TOutputImage >
+CudaInPlaceImageFilter<TInputImage, TOutputImage >
 {
 public:
 
@@ -57,7 +57,7 @@ public:
 
   /** Standard class typedefs. */
   typedef CudaSubtractConstantFromImageFilter  Self;
-  typedef ImageToImageFilter<TInputImage,TOutputImage >
+  typedef CudaInPlaceImageFilter<TInputImage,TOutputImage >
                                              Superclass;
   typedef SmartPointer<Self>        Pointer;
   typedef SmartPointer<const Self>  ConstPointer;
@@ -67,7 +67,7 @@ public:
 
   /** Runtime information support. */
   itkTypeMacro(CudaSubtractConstantFromImageFilter,
-               ImageToImageFilter);
+               CudaInPlaceImageFilter);
 
   typedef typename InputImageType::PixelType   InputPixelType;
   typedef typename OutputImageType::PixelType  OutputPixelType;
@@ -93,7 +93,7 @@ public:
                    typename TOutputImage::PixelType>));
   itkConceptMacro(Input1Input2OutputSubtractOperatorCheck,
                   (Concept::AdditiveOperators<typename TInputImage::PixelType,
-                   TConstant,
+                   InputPixelType,
                    typename TOutputImage::PixelType>));
   /** End concept checking */
 #endif

### 2011-05-06 trunk/Examples/Architecture1/src/SubtractConstantFromImageFilter/CudaSubtractConstantFromImageFilterKernel.cu

@@ -12,27 +12,55 @@
 #include <cuda.h>
 #include <cutil.h>
 
-template <class T>
-__global__ void SubtractConstantFromImageKernel(T *output, int N, T C) {
-	int idx = blockIdx.x * blockDim.x + threadIdx.x;
-	if (idx < N) {
-		output[idx] -= C;
-	}
+template <class S>
+__global__ void SubtractConstantFromImageKernel(S *output, int N, S C)
+{
+   int idx = blockIdx.x * blockDim.x + threadIdx.x;
+   if (idx<N) 
+   {
+      output[idx] -= C;
+   }
 }
 
-float * SubtractConstantFromImageKernelFunction(const float* input1,
-		unsigned int N, float C) {
-	float *output;
-
-	output = const_cast<float*> (input1);
-
-	// Compute execution configuration
-	int blockSize = 128;
-	int nBlocks = N / blockSize + (N % blockSize == 0 ? 0 : 1);
-
-	// Call kernel
-	SubtractConstantFromImageKernel <<< nBlocks, blockSize >>> (output, N, C);
-
-	// Return pointer to the output
-	return output;
+template <class T, class S>
+__global__ void SubtractConstantFromImageKernel(S *output, const T *input, int N, T C)
+{
+   int idx = blockIdx.x * blockDim.x + threadIdx.x;
+   if (idx<N) 
+   {
+      output[idx] = input[idx] - C;
+   }
 }
+
+template<class T, class S>
+void SubtractConstantFromImageKernelFunction(const T* input, S* output, unsigned int N, T C)
+{
+   // Compute execution configuration 
+   int blockSize = 128;
+   int nBlocks = N/blockSize + (N%blockSize == 0?0:1);
+
+
+   // Call kernal
+   if (output == input)
+     SubtractConstantFromImageKernel <<< nBlocks, blockSize >>> (output, N, C);
+   else
+     SubtractConstantFromImageKernel <<< nBlocks, blockSize >>> (output, input, N, C);
+
+}
+
+// versions we wish to compile
+#define THISTYPE float
+template void SubtractConstantFromImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input, THISTYPE * output, unsigned int N, THISTYPE C);
+#undef THISTYPE
+#define THISTYPE int
[…]

### 2011-05-06 trunk/Examples/Architecture1/src/SubtractConstantFromImageFilter/CudaSubtractConstantFromImageFilterKernel.h

@@ -8,5 +8,6 @@
  * File Description:
  *
  */
-float * SubtractConstantFromImageKernelFunction(const float* input1, unsigned int N, float C);
+template <class T, class S> extern
+void SubtractConstantFromImageKernelFunction(const T* input1, S*output, unsigned int N, T C);
 

### 2011-05-06 trunk/Examples/Architecture1/src/SubtractImageFilter/CudaSubtractImageFilter.h

@@ -26,7 +26,7 @@ SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
 #ifndef __itkCudaSubtractImageFilter_h
 #define __itkCudaSubtractImageFilter_h
 
-#include "itkImageToImageFilter.h"
+#include "CudaInPlaceImageFilter.h"
 
 namespace itk
 {
@@ -44,14 +44,14 @@ namespace itk
  *
  * \ingroup IntensityImageFilters CudaEnabled
  *
- * \sa ImageToImageFilter
+ * \sa CudaInPlaceImageFilter
  */
 
 
 template <class TInputImage, class TOutputImage>
 class ITK_EXPORT CudaSubtractImageFilter :
     public
-ImageToImageFilter<TInputImage, TOutputImage >
+CudaInPlaceImageFilter<TInputImage, TOutputImage >
 {
 public:
 
@@ -60,7 +60,7 @@ public:
 
   /** Standard class typedefs. */
   typedef CudaSubtractImageFilter  Self;
-  typedef ImageToImageFilter<TInputImage,TOutputImage >
+  typedef CudaInPlaceImageFilter<TInputImage,TOutputImage >
                                              Superclass;
   typedef SmartPointer<Self>        Pointer;
   typedef SmartPointer<const Self>  ConstPointer;
@@ -70,7 +70,7 @@ public:
 
   /** Runtime information support. */
   itkTypeMacro(CudaSubtractImageFilter,
-               ImageToImageFilter);
+               CudaInPlaceImageFilter);
 
   typedef typename InputImageType::PixelType   InputPixelType;
   typedef typename OutputImageType::PixelType  OutputPixelType;

### 2011-05-06 trunk/article/Article.tex
added example sources
article basics

@@
 \noindent
+There is great interest in the use of graphics processing units (GPU)
+for general purpose applications because the highly parallel
+architectures used in GPUs offer the potential for huge performance
+increases. The use of GPUs in image analysis applications has been
+under investigation for a number of years. This article describes
+modifications to the InsightToolkit (ITK) that provide a simple
+architecture for transparent use of GPU enabled filters and examples
+of how to write GPU enabled filters using the NVIDIA CUDA tools.
+
+This work was performed between late 2009 and early 2010 and is being
+published as patches to ITK 3.20. It is hoped that publication will
+help inform more general development of GPU support in ITK 4.0 and
+facilitate experimentation by users requiring functionality of 3.20 or
+wishing to pursue CUDA based developments.
 \end{abstract}
@@
 \section{Introduction}
+Data must be resident in GPU device memory in order to be processed by
+the GPU. In order for an ITK filter to be accelerated using GPUs an
+image must be copied to the device memory and the result copied back
+if the next filter is not GPU enabled. Copying between host and device
+memory is quite slow and can easily offset any benefits achieved by
+faster GPU processing. It is therefore essential that redundant copies
+between host and device memory are eliminated. It is also desirable
+that new, GPU enabled, filters can be included in applications without
+changing programming style.
+
+This article describes a simple modification to the itk::Image class
+that allows transparent use of CUDA enabled filters. A range of
+standard filters have been implemented and extensive testing
+performed.
+
+\section{CITK Architecture}
+The aim of the architecture outline below was to allow GPU enabled
+filters to be included in an application without change of programming
+style or losing performance via redundant host to device memory copies.
+
+A number of architectures were considered. These were derived from
+online discussions and small samples of code available online:
+\begin{itemize}
+\item Break the pipeline at the beginning of filter execution by
+  copying data to device memory, processing, and then copying back
+  after execution completes. This isolates the GPU code from the rest
+  of the pipeline and requires no change to ITK infrastructure, but
+  introduces redundant copies if subsequent filters are GPU enabled.
+\item Include interface objects between filters in the pipeline to
+  manage copying. This can eliminate redundant copies but requires
+  that the programmer be aware of which filters are GPU enabled. There
+  is also a minor change of programming style.
+\end{itemize}
+
+Neither of these options require a modification to core ITK classes.
+
+The approach used in CITK does require a modification to core ITK
+classes, but has a number of advantages. A similar approach has since
+been outlined on the ITK Wiki {\url http://www.cmake.org/Wiki/ITK_Release_4/GPU_Acceleration}.
+
+The fundamental component of the pipeline is the ITK Image
+class. Within this class is a pixel container called {\em
+  ImportImageContainer}, used to manage the image data. CITK includes
+a substitute pixel container named {\em
+  CudaImportImageContainer}. This pixel container has all the same
+functionality of the {\em ImportImageContainer} which results in full
+compatibility with existing ITK components.
+
+The {\em CudaImportImageContainer} manages image data on both the host
+and device. When a standard filter requests the image data, such as
+through an iterator, the {\em CudaImportImageContainer} checks whether
+the most up to date image is on the device or the host. If it is on
+the device, it is copied back onto the host. This data is then
+supplied to the user. Similarly when a GPU filter requests the image
+data, the {\em CudaImportImageContainer} would check where the most up
+to date image is, and copy it to the device if required.
+
+The {\em CudaImportImageContainer} can track where the most up to the
+date image is by which set command was used last, and assumes the data
+is modified when a standard iterator requests it.
+
+The result of this is memory transfers are only performed when
+required and are completed transparent to both the developer and the
+user. This leaves all the responsibility on the architect, rather than
+the developer or the user such as in the other attempts.
+
+\subsection{Weaknesses}
+\begin{itemize}
+\item This framework only supports Cuda, and not openCL. The ITK 4.0
+proposal supports openCL. Limitations of the Cuda development
+environment mean that even Cuda integration is less complete than
+hoped, with significant changes to compilation processes being
+necessary (see below).
+\item A copy between host and device always results in the source of
+the copy being considered redundant. This could be inefficient in some
+cases. The problem is correctly dealing with identical copies on both
+host and device. If, for example, a pipeline is branched such that one
+branch in on GPU and the other on CPU, then the branch point is likely
+to become a source of redundant copies.
+\item The need to copy between device and host memory breaks some of
+the usual assumptions, leading to some ugly use of {\em mutable}
+declarations in CudaImportImageContainer.
+\end{itemize}
+
+\section{Installation and building}
+\subsection{Cuda compiler and software development kit}
+This framework requires Cuda 3.2 and the SDK.
+\subsection{Patch ITK 3.20}
+The code distributed with this article includes a patch to modify ITK 3.20. This can be applied as follows:
+
+\begin{itemize}
+\item {\url http://voxel.dl.sourceforge.net/sourceforge/itk/InsightToolkit-3.20.0.tar.gz}
+\item extract
+\item cd ITK-3.20
+\item patch -p0 < path/to/patch_3.20.dif
+\end{itemize}
+
+Alternatviely, this code may currently be retrieved via git and gerrit, as follows:
+\begin{itemize}
+\item git clone git://itk.org/ITK.git
+\item cd ITK
+\item git checkout v3.20.0
+\item git pull http://review.source.kitware.com/p/ITK refs/changes/52/1452/1
+\end{itemize}
+
+\subsection{Build and install modified ITK}
+There are many options available when building ITK. This process has
+been tested under Linux and there are a number of changes to defaults
+required to avoid limitations to the cuda development tools. 
+\begin{itemize}
+  \item Specify location of Cuda SDK.
+  \item Turn off SSE options for VNL - advanced/VNL. This avoids errors caused by multiple inclusion of SSE files.
+\end{itemize}
+
+\subsection{Build examples}
+\subsection{Workarounds for nvcc weaknesses/bugs}
+\begin{itemize}
+  \item multiple include of SSE files - turn off SSE options for VNL - advanced/VNL.
+\end{itemize}
+
+\subsection{Changes to standard processes for building ITK applications}
+Typical application development in ITK utilizes templates and generic
+programming and therefore does not require that the developer track
+new object code dependencies when adding new filters. In principle the
+same procedure should be possible when using CUDA enabled devices by
+compiling all application code with nvcc, leading to non-cuda code
+being compiled with the host c++ compiler and cuda code being compiled
+with cuda compilers. This would also allow useful templating of cuda
+kernels, leading to a relatively seamless integration with traditional
+ITK development. Unfortunately the current generation of CUDA tools is
+not able to cope with c++ of the complexity used in ITK. It is
+therefore necessary to compile cuda kernels separately, which means
+the developer must specify the correct object dependencies to the
+linker. Examples of this can be seen in the CMake files included with
+this article.
+
+Alternatives, such as compiling all cuda kernels into a library, are
+feasible but haven't been tested during this development.
+
+\section{Anatomy of a CUDA enabled filter}
+\subsection{Image parameters}
+Different image operations require different image information. Number
+of pixels and image dimensions are all available in the normal way via
+GetSize, GetNumberOfPixels and related methods.
+
+\subsection{Memory management}
+
+Two base classes have been provided to handle standard filter memory
+management - {\em CudaInPlaceImageFilter} and {\em
+CudaImageToImageFilter}. These filters allow the standard allocation
+structure to be used via {\em this->AllocateOutputs()}. Explicit
+allocation of device memory can be achieved using
+Image->AllocateGPU().
+
+\subsection{Templated kernel files}
+ITK filters are generic with respect to pixel type and dimension.
+
+\subsection{Templated kernel file}
+
+%\subsection{}
 
 \bibliographystyle{plain}
-\bibliography{local,InsightJournal}
+%\bibliography{local,InsightJournal}
+\bibliography{InsightJournal}
 \nocite{ITKSoftwareGuide}

### 2011-05-11 article/Article.tex
minor article update
renamed patch file

@@
 of how to write GPU enabled filters using the NVIDIA CUDA tools.
+
+This work was performed between late 2009 and early 2010 and is being
+published as modifications to ITK 3.20. It is hoped that publication will
+help inform more general development of GPU support in ITK 4.0 and
+facilitate experimentation by users requiring functionality of 3.20 or
+wishing to pursue CUDA based developments.
 \end{abstract}
@@
 
-A number of architectures were considered. These were derived from online discussions and small samples of code available online:
+A number of architectures were considered. These were derived from
+online discussions and small samples of code available online:
 \begin{itemize}
@@
 The approach used in CITK does require a modification to core ITK
-classes, but has a number of advantages. The same approach has since
-been outlined on the ITK Wiki.
+classes, but has a number of advantages. A similar approach has since
+been outlined on the ITK Wiki {\url http://www.cmake.org/Wiki/ITK_Release_4/GPU_Acceleration}.
 
-The fundamental component of the pipeline is the ITK Image
+The fundamental component of the pipeline is the {\em itk::Image}
 class. Within this class is a pixel container called {\em
@@
 
-The {\em CudaImportImageContainer} not only managed the image data on
-the host, but it also managed the image data on the device. When a
-standard filter requested the image data, such as through an iterator,
-the {\em CudaImportImageContainer} checks whether the most up to date
-image is on the device or the host. If it is on the device, it is
-copied back onto the host. This data is then supplied to the
-user. Similarly when a GPU filter requests the image data, the {\em
-  CudaImportImageContainer} would check where the most up to date
-image is, and copy it to the device if required.
+The {\em CudaImportImageContainer} manages image data on both the host
+and device. When a standard filter requests the image data, such as
+through an iterator, the {\em CudaImportImageContainer} checks whether
+the most up to date image is on the device or the host. If it is on
+the device, it is copied back onto the host. This data is then
+supplied to the user. Similarly when a GPU filter requests the image
+data, the {\em CudaImportImageContainer} would check where the most up
+to date image is, and copy it to the device if required.
 
@@
 
+\subsection{Weaknesses}
+\begin{itemize}
+\item This framework only supports Cuda, and not OpenCL. The ITK 4.0
+proposal supports OpenCL. Limitations of the Cuda development
+environment mean that even Cuda integration is less complete than
+hoped, with significant changes to compilation processes being
+necessary (see below).
+\item A copy between host and device always results in the source of
+the copy being considered redundant. This could be inefficient in some
+cases. The problem is correctly dealing with identical copies on both
+host and device. If, for example, a pipeline is branched such that one
+branch in on GPU and the other on CPU, then the branch point is likely
+to become a source of redundant copies.
+\item The need to copy between device and host memory breaks some of
+the usual assumptions, leading to some ugly use of {\em mutable}
+declarations in CudaImportImageContainer.
+\item Morphology filters included in the package use texture memory
+but are not as generic as the standard ITK versions.
+\end{itemize}
+
+\section{Installation and building}
+\subsection{Cuda compiler and software development kit}
+This framework requires Cuda 3.2 and the SDK.
+\subsection{Patch ITK 3.20}
+The code distributed with this article includes a patch to modify ITK 3.20. This can be applied as follows:
+
+\begin{itemize}
+\item {\url http://voxel.dl.sourceforge.net/sourceforge/itk/InsightToolkit-3.20.0.tar.gz}
+\item extract
+\item cd ITK-3.20
+\item patch -p0 < path/to/patch_3.20.dif
+\end{itemize}
+
+Alternatviely, this code may currently be retrieved via git and gerrit, as follows:
+\begin{itemize}
+\item git clone git://itk.org/ITK.git
+\item cd ITK
+\item git checkout v3.20.0
+\item git pull http://review.source.kitware.com/p/ITK refs/changes/52/1452/1
+\end{itemize}
+
+\subsection{Build and install modified ITK}
+There are many options available when building ITK. This process has
+been tested under Linux and there are a number of changes to defaults
+required to avoid limitations to the cuda development tools. 
+\begin{itemize}
+  \item Specify location of Cuda SDK.
+  \item Turn off SSE options for VNL - advanced/VNL. This avoids errors caused by multiple inclusion of SSE files.
+\end{itemize}
+
+\subsection{Build examples}
+\subsection{Workarounds for nvcc weaknesses/bugs}
+\begin{itemize}
+  \item multiple include of SSE files - turn off SSE options for VNL - advanced/VNL.
+\end{itemize}
+
+\subsection{Changes to standard processes for building ITK applications}
+Typical application development in ITK utilizes templates and generic
+programming and therefore does not require that the developer track
+new object code dependencies when adding new filters. In principle the
+same procedure should be possible when using CUDA enabled devices by
+compiling all application code with nvcc, leading to non-cuda code
+being compiled with the host c++ compiler and cuda code being compiled
+with cuda compilers. This would also allow useful templating of cuda
+kernels, leading to a relatively seamless integration with traditional
+ITK development. Unfortunately the current generation of CUDA tools is
+not able to cope with c++ of the complexity used in ITK. It is
+therefore necessary to compile cuda kernels separately, which means
+the developer must specify the correct object dependencies to the
+linker. Examples of this can be seen in the CMake files included with
+this article.
+
+Alternatives, such as compiling all cuda kernels into a library, are
+feasible but haven't been tested during this development.
+
 \section{Anatomy of a CUDA enabled filter}
@@
 
-Your CUDA kernel function should return a pointer to the output image as a global device pointer:
+Two base classes have been provided to handle standard filter memory
+management - {\em CudaInPlaceImageFilter} and {\em
+CudaImageToImageFilter}. These filters allow the standard allocation
+structure to be used via {\em this->AllocateOutputs()}. Explicit
+allocation of device memory can be achieved using
+Image->AllocateGPU().
 
-{\tt typename TOutputImage::PixelType * ptr;}
-
-A pointer to input image memory is retrieved using:
-
-{\tt input->GetDevicePointer();}
-
-After the filter has completed, the output pointer must be given to
-the output image to be passed down the pipeline:
-
-{\tt output->GetPixelContainer()->SetDevicePointer(ptr, N, true);}
-
-In this example the {\tt ptr} is the pointer to output memory and the 'N'
-is the number of pixels in this image. The 'true' value is very
-important. This tells the output image to free the device memory once
-it is finished with it. WARNING: Setting this to false can lead to
-memory leaks on the device.
+\subsection{Templated kernel files}
+ITK filters are generic with respect to pixel type and dimension.
 

### 2011-05-17 article/Article.tex
preparing for more work on docs

@@
 \begin{itemize}
-\item This framework only supports Cuda, and not OpenCL. The ITK 4.0
-proposal supports OpenCL. Limitations of the Cuda development
-environment mean that even Cuda integration is less complete than
+\item This framework only supports CUDA, and not OpenCL. The ITK 4.0
+proposal supports OpenCL. Limitations of the CUDA development
+environment mean that even CUDA integration is less complete than
 hoped, with significant changes to compilation processes being
@@
 but are not as generic as the standard ITK versions.
+\item ITK filters are able to provide their own implementations of key
+methods, such as {\em AllocateOutputs}. This can lead to problems when
+connecting CUDA enabled components to a CPU pipeline. This problem has
+been observed in the {\em itkStatisticsImageFilter}, which is a
+multi-threaded {\em ImageToImageFilter} with its own AllocateOutputs
+method passing input through to output. This bypasses the trigger to
+copy device memory back to the host, leading to incorrect results.
 \end{itemize}
@@
 \section{Installation and building}
-\subsection{Cuda compiler and software development kit}
-This framework requires Cuda 3.2 and the SDK.
+\subsection{CUDA compiler and software development kit}
+This framework requires CUDA 3.2 and the SDK. The {\em thrust} library
+is also included in the examples to implement more complex components
+of some sample filters.
 \subsection{Patch ITK 3.20}
@@
 \item cd ITK-3.20
-\item patch -p0 < path/to/patch_3.20.dif
+\item patch -p0 < path/to/patch.3.20.0.dif
 \end{itemize}
 
-Alternatviely, this code may currently be retrieved via git and gerrit, as follows:
+Alternatviely, this code may currently be retrieved via git, as follows:
 \begin{itemize}
-\item git clone git://itk.org/ITK.git
+\item git clone git://github.com/richardbeare/ITK.git
 \item cd ITK
 \item git checkout v3.20.0
-\item git pull http://review.source.kitware.com/p/ITK refs/changes/52/1452/1
+\item git branch v3.20.0_cuda
 \end{itemize}
@@
 been tested under Linux and there are a number of changes to defaults
-required to avoid limitations to the cuda development tools. 
+required to avoid limitations to the CUDA development tools. 
 \begin{itemize}
-  \item Specify location of Cuda SDK.
+  \item Specify location of CUDA SDK.
   \item Turn off SSE options for VNL - advanced/VNL. This avoids errors caused by multiple inclusion of SSE files.
@@
 same procedure should be possible when using CUDA enabled devices by
-compiling all application code with nvcc, leading to non-cuda code
-being compiled with the host c++ compiler and cuda code being compiled
-with cuda compilers. This would also allow useful templating of cuda
+compiling all application code with nvcc, leading to non-CUDA code
+being compiled with the host c++ compiler and CUDA code being compiled
+with CUDA compilers. This would also allow useful templating of CUDA
 kernels, leading to a relatively seamless integration with traditional
@@
 not able to cope with c++ of the complexity used in ITK. It is
-therefore necessary to compile cuda kernels separately, which means
+therefore necessary to compile CUDA kernels separately, which means
 the developer must specify the correct object dependencies to the
@@
 
-Alternatives, such as compiling all cuda kernels into a library, are
+This approach also implies that the CUDA kernels need to be compiled
+for the appropriate types, and this is currently achieved using a set
+of macros supporting a limited range of input and output
+types. Compiling application code with nvcc would eliminate these
+macros.
+
+Alternatives, such as compiling all CUDA kernels into a library, are
 feasible but haven't been tested during this development.
@@
 \section{Anatomy of a CUDA enabled filter}
-\subsection{Image parameters}
-Different image operations require different image information. Number
-of pixels and image dimensions are all available in the normal way via
-GetSize, GetNumberOfPixels and related methods.
+CUDA enabled filters can look very like a conventional ITK filter,
+with the main difference being a call to a CUDA kernel function from
+within the {\em GenerateData} method. CUDA-enabled filters should
+never have {\em ThreadedGenerateData} methods as threading is provided
+within the CUDA portion.
 
 \subsection{Memory management}
-
 Two base classes have been provided to handle standard filter memory
@@
 allocation of device memory can be achieved using
-Image->AllocateGPU().
+{\em Image->AllocateGPU()}
 
 \subsection{Templated kernel files}
-ITK filters are generic with respect to pixel type and dimension.
+ITK filters are generic with respect to pixel type and dimension and
+hence CUDA kernels should offer the same flexibility. This is not
+currently possible. The structure outlined in this section is the best
+approximation we have been able to achieve and we hope it will evolve
+to be better integrated with ITK as the CUDA tools improve.
 
-\subsection{Templated kernel file}
+Each kernel function has a declaration - e.g. CudaAddImageFilterKernel.h contains
+\begin{verbatim}
+template <class T, class S> extern
+void AddImageKernelFunction(const T* input1, const T* input2, S* output, unsigned int N);
+\end{verbatim}
 
-%\subsection{}
+The corresponding CudaAddImageFilterKernel.cu file contains:
+\begin{verbatim}
+template <class T, class S>
+__global__ void AddImageKernel(T *output, const S *input, int N)
+{
+  int idx = blockIdx.x * blockDim.x + threadIdx.x;
+  if (idx<N) 
+    {
+    output[idx] += input[idx];
+    }
+}
+
+template <class T, class S>
+__global__ void AddImageKernel(T *output, const S *input1, const S* input2, int N)
+{
+   int idx = blockIdx.x * blockDim.x + threadIdx.x;
+   if (idx<N) 
+     {
+     output[idx] = input1[idx] + input2[idx];
+     }
+}
+
+template <class T, class S>
+void AddImageKernelFunction(const T* input1, const T* input2, S* output, unsigned int N)
+{
+
+    // Compute execution configuration 
+    int blockSize = 128;
+    int nBlocks = N/blockSize + (N%blockSize == 0?0:1);
+
+    // Call kernels optimized for in place filtering
+    if (output == input1)
+      AddImageKernel <<< nBlocks, blockSize >>> (output, input2, N);
+    else
+      AddImageKernel <<< nBlocks, blockSize >>> (output, input1, input2, N);
+}
+
+#define THISTYPE float
+template void AddImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, const THISTYPE * input2, THISTYPE * output, unsigned int N);
+#undef THISTYPE
+#define THISTYPE int
+template void AddImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, const THISTYPE * input2, THISTYPE *output, unsigned int N);
+#undef THISTYPE
+
+#define THISTYPE short
+template void AddImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, const THISTYPE * input2, THISTYPE *output, unsigned int N);
+#undef THISTYPE
+
+#define THISTYPE unsigned char
+template void AddImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, const THISTYPE * input2,  THISTYPE *output, unsigned int N);
+#undef THISTYPE
+
+\end{verbatim}
+
+This is a simple structure that allows a number kernels to be precompiled for different voxel types.
 

### 2011-05-17 trunk/Examples/Architecture1/src/AddConstantToImageFilter/CudaAddConstantToImageFilterKernel.cu
completed performance tests

@@ -1,18 +1,9 @@
-/*
- * File Name:    cuda-kernel.cu
- *
- * Author:        Phillip Ward
- * Creation Date: Monday, January 18 2010, 10:00 
- * Last Modified: Wednesday, December 23 2009, 16:35 
- * 
- * File Description:
- *
- */
+
 #include <stdio.h>
 #include <cuda.h>
 #include <cutil.h>
 
-#include <thrust/transform.h>
+#ifndef CITK_USE_THRUST
 
 template <class S>
 __global__ void AddConstantToImageKernel(S *output, int N, S C)
@@ -41,7 +32,6 @@ void AddConstantToImageKernelFunction(const T* input, S* output, unsigned int N,
    int blockSize = 128;
    int nBlocks = N/blockSize + (N%blockSize == 0?0:1);
 
-
    // Call kernel
    if (output == input)
      AddConstantToImageKernel <<< nBlocks, blockSize >>> (output, N, C);
@@ -50,27 +40,32 @@ void AddConstantToImageKernelFunction(const T* input, S* output, unsigned int N,
 
 }
 
-// template <typename S>
-// struct addC
-// {
-//     const S a;
+#else
+#include "thrust/transform.h"
 
-//     addC(S _a) : a(_a) {}
+template <typename S>
+struct addC
+{
+  const S a;
 
-//     __host__ __device__
-//         S operator()(const float& x) const { 
-//             return a + x;
-//         }
-// };
+  addC(S _a) : a(_a) {}
 
-// template<class T, class S>
-// void AddConstantToImageKernelFunction(const T* input, S* output, unsigned int N, T C)
-// {
-//   thrust::device_ptr<const T> i1(input);
-//   thrust::device_ptr<S> o1(output);
-//   thrust::transform(i1, i1 + N, o1, addC<S>(C));
+  __host__ __device__
+  S operator()(const float& x) const { 
+    return a + x;
+  }
+};
 
-// }
+template<class T, class S>
+void AddConstantToImageKernelFunction(const T* input, S* output, unsigned int N, T C)
+{
+  thrust::device_ptr<const T> i1(input);
+  thrust::device_ptr<S> o1(output);
+  thrust::transform(i1, i1 + N, o1, addC<S>(C));
+
+}
+
+#endif
 // versions we wish to compile
 #define THISTYPE float
 template void AddConstantToImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input, THISTYPE * output, unsigned int N, THISTYPE C);

### 2011-05-17 trunk/Examples/Architecture1/src/StatisticsImageFilter/CudaStatisticsImageFilter.h

@@ -3,7 +3,7 @@
 #ifndef __itkCudaStatisticsImageFilter_h
 #define __itkCudaStatisticsImageFilter_h
 
-#include "itkImageToImageFilter.h"
+#include "itkInPlaceImageFilter.h"
 #include "itkNumericTraits.h"
 #include "itkSimpleDataObjectDecorator.h"
 
@@ -22,7 +22,8 @@ namespace itk {
  * threaded. It computes statistics in each thread then combines them in
  * its AfterThreadedGenerate method.
  *
- * \author Phillip Ward, Victorian Partnership for Advanced Computing (VPAC)
+ * \author Phillip Ward, Victorian Partnership for Advanced Computing
+ * (VPAC).Richard Beare
  *
  * \ingroup MathematicalStatisticsImageFilters CudaEnabled
  *

### 2011-05-17 article/Article.tex
minor article updates

@@
 % subfigures
-\usepackage{subfigure}
+%\usepackage{subfigure}
 
@@
 % snail-mail address if you like.
-\author{Richard Beare{$^1$}, Daniel Micevski, Chris Share\\Luke Parkinson, Phillip Ward, Mike Kuiper{$^2$}}
+\author{Richard Beare{$^1$}, Daniel Micevski, Chris Share\\Luke
+  Parkinson, Phillip Ward, Wojtek Goscinski{$1$}, Mike Kuiper{$^2$}}
 \authoraddress{{$^1$}Richard.Beare@monash.edu, Monash University, Melbourne, Australia\\
@@
 \section{CITK Architecture}
-The aim of the architecture outline below was to allow GPU enabled
+The aim of the architecture outlined below was to allow GPU enabled
 filters to be included in an application without change of programming
@@
 classes, but has a number of advantages. A similar approach has since
-been outlined on the ITK Wiki {\url http://www.cmake.org/Wiki/ITK_Release_4/GPU_Acceleration}.
+been outlined on the ITK Wiki \url{http://www.cmake.org/Wiki/ITK\_Release\_4/GPU\_Acceleration}.
 
@@
 
+Some exceptions have been uncovered during this development. Minor
+changes have also been made to the {\em AllocateOutputs} method of the
+{\em itkInPlaceImageFilter} to support pipelines that connect in
+place, multi-threaded CPU filters to a CUDA filter. Other exceptions
+are discussed below.
+
 \subsection{Weaknesses}
@@
 method passing input through to output. This bypasses the trigger to
-copy device memory back to the host, leading to incorrect results.
+copy device memory back to the host, leading to incorrect
+results. Other filters with unusual structure are likely to cause
+problems. The simple fix for such filters is to call {\em
+  GetBufferPointer} in the {\em AllocateOutputs} method.
 \end{itemize}
@@
 \begin{itemize}
-\item {\url http://voxel.dl.sourceforge.net/sourceforge/itk/InsightToolkit-3.20.0.tar.gz}
+\item \url{http://voxel.dl.sourceforge.net/sourceforge/itk/InsightToolkit-3.20.0.tar.gz}
 \item extract
 \item cd ITK-3.20
-\item patch -p0 < path/to/patch.3.20.0.dif
+\item patch -p0 $<$ path/to/patch.3.20.0.dif 
 \end{itemize}
@@
 \item cd ITK
-\item git checkout v3.20.0
-\item git branch v3.20.0_cuda
+\item git checkout v3.20.0\_cuda
 \end{itemize}
@@
 \subsection{Build examples}
-\subsection{Workarounds for nvcc weaknesses/bugs}
-\begin{itemize}
-  \item multiple include of SSE files - turn off SSE options for VNL - advanced/VNL.
-\end{itemize}
+The examples and tests are included in this package. The most up to
+date version of the package can be found at \url{http://code.google.com/p/cuda-insight-toolkit/}.
 
@@
 
+Pointers to device memory are obtained using the {\em
+  GetDevicePointer} method and are passed to CUDA kernel functions.
+
 \subsection{Memory management}
@@
 The corresponding CudaAddImageFilterKernel.cu file contains:
+{\small
 \begin{verbatim}
@@
 #define THISTYPE float
-template void AddImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, const THISTYPE * input2, THISTYPE * output, unsigned int N);
+template void AddImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, 
+                                                         const THISTYPE * input2, 
+                                                         THISTYPE * output, unsigned int N);
 #undef THISTYPE
 #define THISTYPE int
-template void AddImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, const THISTYPE * input2, THISTYPE *output, unsigned int N);
+template void AddImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, 
+                                                         const THISTYPE * input2,
+                                                         THISTYPE *output, unsigned int N);
 #undef THISTYPE
@@
 #define THISTYPE short
-template void AddImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, const THISTYPE * input2, THISTYPE *output, unsigned int N);
+template void AddImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1,
+                                                         const THISTYPE * input2,
+                                                         THISTYPE *output, unsigned int N);
 #undef THISTYPE
@@
 #define THISTYPE unsigned char
-template void AddImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, const THISTYPE * input2,  THISTYPE *output, unsigned int N);
+template void AddImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, 
+                                                         const THISTYPE * input2,
+                                                         THISTYPE *output, unsigned int N);
 #undef THISTYPE
@@
 \end{verbatim}
+}
+This is a simple structure that allows a number kernels to be precompiled for different voxel types.
 
-This is a simple structure that allows a number kernels to be precompiled for different voxel types.
+\subsection{Using {\em thrust} algorithms}
+The thrust project, \url{http://code.google.com/p/thrust/}, is a
+source of templated, CUDA-enabled algorithms. The
+CudaStatisticsImageFilter makes use of these algorithms. It is also
+possible to implement simple arithmetic filters using the thrust {\em
+  transform} algorithm (leading to more elegant code), but preliminary
+tests suggest a significant loss in performance. There are
+examples of thrust-based arithmetic in several sample filters that can
+be switched on with a cmake option.
+
+\section{Testing}
+The online testing within the Insight Journal does not support CUDA
+and therefore cannot be used to test this contribution.
+\subsection{ITK}
+Changes to ITK classes have been tested using standard ITK tests,
+producing the same results as an unmodified ITK.
+\subsection{Testing CUDA filters}
+A range of simple CUDA enabled filters have been developed and
+compared to the CPU equivalents. CMake based test are included in this
+contribution.
+
+\section{Performance}
+Improved computational performance is the reason for interest in GPU
+imaging applications. However there are many stories of how difficult
+this is to achieve in practice, and similar difficulties are likely to
+be experienced in the imaging domain. Some of the difficulties we
+forsee are:
+\begin{itemize}
+\item A real imaging application is likely to utilize a large number
+  of ITK filters. It is likely to be a long time before a significant
+  portion of ITK is CUDA (or GPU) enabled. Therefore a developer will
+  only experience a nett performance gain if the CUDA enabled filter
+  offers sufficient speedup to offset memory transfer costs and a
+  small proportion of the application is particularly time consuming.
+\item Filters that are easy to port to the GPU tend to be fast on CPU
+  anyway, and typically don't represent a large proportion of
+  application time. Examples include all voxel-wise operations, such
+  as masking and arithmetic.
+\item Many potentially time consuming operations, such as filtering
+  with large kernels, have been highly optimised for CPU
+  implementation. It is important the comparisons are made with these
+  optimised CPU implementations.
+\end{itemize}
+
+We won't discuss the mechanics of CUDA performance profiling in this
+article - there are many resources available online.
+
+One point worth noting when testing CUDA enabled ITK filters is that
+there is a per-process cost associated with running a CUDA-enabled
+application. This cost appears to relate to a number of things,
+including loading libraries and initializing the device. This cost can
+be very significant - as much as 2.5 seconds on one of our test
+machines - and can give an exagerated negative impression of the  filter
+performance.
+
+Finally, some positive performance results. These tests were carried
+out using a Tesla T10 in a 16 core, 2261.051MHz, Intel L5520  Xeon:
+\begin{itemize}
+\item Performance improvement of 190 times observed with simple arithmetic, such as adding or subtracting constants from
+  images. See {\em simple\_perf\_test.cxx} for details.
+\item Image filtering with kernels, for example simple means, offer ??
+  for 3d kernels, radius 10 voxels on images size $500 \times 500
+  \times 500$. This is potentially interesting for applications
+  requiring kernels of specific shape, because most accelerated CPU
+  schemes can only implement a restricted range of shape kernels. The
+  accelerated CPU scheme used in this test uses a box filtering
+  approach that is limited to rectangular filters.
+\end{itemize}
+
+\section{Conclusions}
+We have provided some simple modifications to ITK infrastructure that
+allow integration of CUDA enabled filters with ITK applications, and
+provided a number of examples and validation tests. We hope this
+framework will encourage immediate experimentation with GPU filters
+and inform some of the GPU development scheduled for ITK 4.
 

### 2011-05-20 trunk/article/Article.tex
Moving examples around

@@
 % snail-mail address if you like.
-\author{Richard Beare{$^1$}, Daniel Micevski, Chris Share\\Luke Parkinson, Phillip Ward, Mike Kuiper{$^2$}}
+\author{Richard Beare{$^1$}, Daniel Micevski, Chris Share\\Luke
+  Parkinson, Phil Ward, Wojtek Goscinski{$1$}, Mike Kuiper{$^2$}}
 \authoraddress{{$^1$}Richard.Beare@monash.edu, Monash University, Melbourne, Australia\\
@@
 This work was performed between late 2009 and early 2010 and is being
-published as patches to ITK 3.20. It is hoped that publication will
-help inform more general development of GPU support in ITK 4.0 and
+published as modifications to ITK 3.20. It is hoped that publication will
+help inform development of more general GPU support in ITK 4.0 and
 facilitate experimentation by users requiring functionality of 3.20 or
@@
 classes, but has a number of advantages. A similar approach has since
-been outlined on the ITK Wiki {\url http://www.cmake.org/Wiki/ITK_Release_4/GPU_Acceleration}.
+been outlined on the ITK Wiki \url{http://www.cmake.org/Wiki/ITK\_Release\_4/GPU\_Acceleration}.
 
-The fundamental component of the pipeline is the ITK Image
+The fundamental component of the pipeline is the {\em itk::Image}
 class. Within this class is a pixel container called {\em
@@
 
+Some exceptions have been uncovered during this development. Minor
+changes have also been made to the {\em AllocateOutputs} method of the
+{\em itkInPlaceImageFilter} to support pipelines that connect in
+place, multi-threaded CPU filters to a CUDA filter. Other exceptions
+are discussed below.
+
 \subsection{Weaknesses}
 \begin{itemize}
-\item This framework only supports Cuda, and not openCL. The ITK 4.0
-proposal supports openCL. Limitations of the Cuda development
-environment mean that even Cuda integration is less complete than
+\item This framework only supports CUDA, and not OpenCL. The ITK 4.0
+proposal supports OpenCL. Limitations of the CUDA development
+environment mean that even CUDA integration is less complete than
 hoped, with significant changes to compilation processes being
@@
 declarations in CudaImportImageContainer.
+\item Morphology filters included in the package use texture memory
+but are not as generic as the standard ITK versions.
+\item ITK filters are able to provide their own implementations of key
+methods, such as {\em AllocateOutputs}. This can lead to problems when
+connecting CUDA enabled components to a CPU pipeline. This problem has
+been observed in the {\em itkStatisticsImageFilter}, which is a
+multi-threaded {\em ImageToImageFilter} with its own AllocateOutputs
+method passing input through to output. This bypasses the trigger to
+copy device memory back to the host, leading to incorrect
+results. Other filters with unusual structure are likely to cause
+problems. The simple fix for such filters is to call {\em
+  GetBufferPointer} in the {\em AllocateOutputs} method.
 \end{itemize}
@@
 \section{Installation and building}
-\subsection{Cuda compiler and software development kit}
-This framework requires Cuda 3.2 and the SDK.
+\subsection{CUDA compiler and software development kit}
+This framework requires CUDA 3.2 and the SDK. The {\em thrust} library
+is also included in the examples to implement more complex components
+of some sample filters.
 \subsection{Patch ITK 3.20}
-The code distributed with this article includes a patch to modify ITK 3.20. This can be applied as follows:
+The code distributed with this article includes a patch to modify ITK
+3.20, called {\em patch.3.20.0.dif}. This can be applied as follows:
 
 \begin{itemize}
-\item {\url http://voxel.dl.sourceforge.net/sourceforge/itk/InsightToolkit-3.20.0.tar.gz}
+\item fetch \url{http://voxel.dl.sourceforge.net/sourceforge/itk/InsightToolkit-3.20.0.tar.gz}
 \item extract
 \item cd ITK-3.20
-\item patch -p0 < path/to/patch_3.20.dif
+\item patch -p0 $<$ path/to/patch.3.20.0.dif
 \end{itemize}
 
-Alternatviely, this code may currently be retrieved via git and gerrit, as follows:
+Alternatviely, this code may currently be retrieved via git, as follows:
 \begin{itemize}
-\item git clone git://itk.org/ITK.git
+\item git clone git://github.com/richardbeare/ITK.git
 \item cd ITK
-\item git checkout v3.20.0
-\item git pull http://review.source.kitware.com/p/ITK refs/changes/52/1452/1
+\item git checkout v3.20.0\_cuda
 \end{itemize}
@@
 been tested under Linux and there are a number of changes to defaults
-required to avoid limitations to the cuda development tools. 
+required to avoid limitations to the CUDA development tools. 
 \begin{itemize}
-  \item Specify location of Cuda SDK.
-  \item Turn off SSE options for VNL - advanced/VNL. This avoids errors caused by multiple inclusion of SSE files.
+  \item Specify location of CUDA SDK.
+  \item Turn off SSE options for VNL - see advanced/VNL. This avoids errors caused by multiple inclusion of SSE files.
 \end{itemize}
@@
 \section{Anatomy of a CUDA enabled filter}
-\subsection{Image parameters}
-Different image operations require different image information. Number
-of pixels and image dimensions are all available in the normal way via
-GetSize, GetNumberOfPixels and related methods.
+CUDA enabled filters can look very like a conventional ITK filter,
+with the main difference being a call to a CUDA kernel function from
+within the {\em GenerateData} method. CUDA-enabled filters should
+never have {\em ThreadedGenerateData} methods as threading is provided
+within the CUDA portion.
+
+Pointers to device memory are obtained using the {\em
+  GetDevicePointer} method and are passed to CUDA kernel functions.
 
 \subsection{Memory management}
-
 Two base classes have been provided to handle standard filter memory
@@
 allocation of device memory can be achieved using
-Image->AllocateGPU().
+{\em Image->AllocateGPU()}
 
 \subsection{Templated kernel files}
-ITK filters are generic with respect to pixel type and dimension.
+ITK filters are generic with respect to pixel type and dimension and
+hence CUDA kernels should offer the same flexibility. This is not
+currently possible. The structure outlined in this section is the best
+approximation we have been able to achieve and we hope it will evolve
+to be better integrated with ITK as the CUDA tools improve.
 
-\subsection{Templated kernel file}
+Each kernel function has a declaration - e.g. CudaAddImageFilterKernel.h contains
+\begin{verbatim}
+template <class T, class S> extern
+void AddImageKernelFunction(const T* input1, const T* input2, S* output, unsigned int N);
+\end{verbatim}
 
-%\subsection{}
+The corresponding CudaAddImageFilterKernel.cu file contains:
+{\small
+\begin{verbatim}
+template <class T, class S>
+__global__ void AddImageKernel(T *output, const S *input, int N)
+{
+  int idx = blockIdx.x * blockDim.x + threadIdx.x;
+  if (idx<N) 
+    {
+    output[idx] += input[idx];
+    }
+}
+
+template <class T, class S>
+__global__ void AddImageKernel(T *output, const S *input1, const S* input2, int N)
+{
+   int idx = blockIdx.x * blockDim.x + threadIdx.x;
+   if (idx<N) 
+     {
+     output[idx] = input1[idx] + input2[idx];
+     }
+}
+
+template <class T, class S>
+void AddImageKernelFunction(const T* input1, const T* input2, S* output, unsigned int N)
+{
+
+    // Compute execution configuration 
+    int blockSize = 128;
+    int nBlocks = N/blockSize + (N%blockSize == 0?0:1);
+
+    // Call kernels optimized for in place filtering
+    if (output == input1)
+      AddImageKernel <<< nBlocks, blockSize >>> (output, input2, N);
+    else
+      AddImageKernel <<< nBlocks, blockSize >>> (output, input1, input2, N);
+}
+
+#define THISTYPE float
+template void AddImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, 
+                                                         const THISTYPE * input2, 
+                                                         THISTYPE * output, unsigned int N);
+#undef THISTYPE
+#define THISTYPE int
+template void AddImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, 
+                                                         const THISTYPE * input2,
+                                                         THISTYPE *output, unsigned int N);
+#undef THISTYPE
+
+#define THISTYPE short
+template void AddImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1,
+                                                         const THISTYPE * input2,
+                                                         THISTYPE *output, unsigned int N);
+#undef THISTYPE
+
+#define THISTYPE unsigned char
+template void AddImageKernelFunction<THISTYPE, THISTYPE>(const THISTYPE * input1, 
+                                                         const THISTYPE * input2,
+                                                         THISTYPE *output, unsigned int N);
+#undef THISTYPE
+
+\end{verbatim}
+}
+This is a simple structure that allows a number kernels to be precompiled for different voxel types.
+
+\subsection{Using {\em thrust} algorithms}
+The thrust project, \url{http://code.google.com/p/thrust/}, is a
+source of templated, CUDA-enabled algorithms. The
+CudaStatisticsImageFilter makes use of these algorithms. It is also
+possible to implement simple arithmetic filters using the thrust {\em
+  transform} algorithm (leading to more elegant code), but preliminary
+tests suggest a significant loss in performance. There are
+examples of thrust-based arithmetic in several sample filters that can
+be switched on with a cmake option.
+
+\section{Testing}
+The online testing within the Insight Journal does not support CUDA
+and therefore cannot be used to test this contribution.
+\subsection{ITK}
+Changes to ITK classes have been tested using standard ITK tests,
+producing the same results as an unmodified ITK.
+\subsection{Testing CUDA filters}
+A range of simple CUDA enabled filters have been developed and
+compared to the CPU equivalents. CMake based test are included in this
+contribution.
+
+\section{Performance}
+Improved computational performance is the reason for interest in GPU
+imaging applications. However there are many stories of how difficult
+this is to achieve in practice, and similar difficulties are likely to
+be experienced in the imaging domain. Some of the difficulties we
+forsee are:
+\begin{itemize}
+\item A real imaging application is likely to utilize a large number
+  of ITK filters. It is likely to be a long time before a significant
+  portion of ITK is CUDA (or GPU) enabled. Therefore a developer will
+  only experience a nett performance gain if the CUDA enabled filter
+  offers sufficient speedup to offset memory transfer costs and a
+  small proportion of the application is particularly time consuming.
+\item Filters that are easy to port to the GPU tend to be fast on CPU
+  anyway, and typically don't represent a large proportion of
+  application time. Examples include all voxel-wise operations, such
+  as masking and arithmetic.
+\item Many potentially time consuming operations, such as filtering
+  with large kernels, have been highly optimised for CPU
+  implementation. It is important the comparisons are made with these
+  optimised CPU implementations.
+\end{itemize}
+
+We won't discuss the mechanics of CUDA performance profiling in this
+article - there are many resources available online.
+
+One point worth noting when testing CUDA enabled ITK filters is that
+there is a per-process cost associated with running a CUDA-enabled
+application. This cost appears to relate to a number of things,
+including loading libraries and initializing the device. This cost can
+be very significant - as much as 2.5 seconds on one of our test
+machines - and can give an exagerated negative impression of the  filter
+performance.
+
+Finally, some positive performance results. These tests were carried
+out using a Tesla T10 in a 16 core, 2261.051MHz, Intel L5520  Xeon:
+\begin{itemize}
+\item Performance improvement of 190 times observed with simple arithmetic, such as adding or subtracting constants from
+  images. See {\em simple\_perf\_test.cxx} for details.
+\item Image filtering with kernels, for example simple means, offer ??
+  for 3d kernels, radius 10 voxels on images size $500 \times 500
+  \times 500$. This is potentially interesting for applications
+  requiring kernels of specific shape, because most accelerated CPU
+  schemes can only implement a restricted range of shape kernels. The
+  accelerated CPU scheme used in this test uses a box filtering
+  approach that is limited to rectangular filters.
+\end{itemize}
+
+\section{Conclusions}
+We have provided some simple modifications to ITK infrastructure that
+allow integration of CUDA enabled filters with ITK applications, and
+provided a number of examples and validation tests. We hope this
+framework will encourage immediate experimentation with GPU filters
+and inform some of the GPU development scheduled for ITK 4.
 

### 2011-05-20 article/Article.tex
article update

@@
 \author{Richard Beare{$^1$}, Daniel Micevski, Chris Share\\Luke
-  Parkinson, Phillip Ward, Wojtek Goscinski{$1$}, Mike Kuiper{$^2$}}
+  Parkinson, Phil Ward, Wojtek Goscinski{$1$}, Mike Kuiper{$^2$}}
 \authoraddress{{$^1$}Richard.Beare@monash.edu, Monash University, Melbourne, Australia\\
@@
 published as modifications to ITK 3.20. It is hoped that publication will
-help inform more general development of GPU support in ITK 4.0 and
+help inform development of more general GPU support in ITK 4.0 and
 facilitate experimentation by users requiring functionality of 3.20 or
@@
 of some sample filters.
+\subsection{Fetch this contribution from google code}
+The source code is included with this article and is also available from google code:
+\url{http://code.google.com/p/cuda-insight-toolkit/}. The patch for ITK is included.
+
 \subsection{Patch ITK 3.20}
-The code distributed with this article includes a patch to modify ITK 3.20. This can be applied as follows:
+The code distributed with this article includes a patch to modify ITK
+3.20, called {\em patch.3.20.0.dif}. This can be applied as follows:
 
 \begin{itemize}
-\item \url{http://voxel.dl.sourceforge.net/sourceforge/itk/InsightToolkit-3.20.0.tar.gz}
+\item fetch \url{http://voxel.dl.sourceforge.net/sourceforge/itk/InsightToolkit-3.20.0.tar.gz}
 \item extract
 \item cd ITK-3.20
-\item patch -p0 $<$ path/to/patch.3.20.0.dif 
+\item patch -p0 $<$ path/to/cuda-insight-toolkit/patch.3.20.0.dif
 \end{itemize}
@@
   \item Specify location of CUDA SDK.
-  \item Turn off SSE options for VNL - advanced/VNL. This avoids errors caused by multiple inclusion of SSE files.
+  \item Turn off SSE options for VNL - see advanced/VNL. This avoids errors caused by multiple inclusion of SSE files.
 \end{itemize}
@@
 \subsection{Build examples}
-The examples and tests are included in this package. The most up to
-date version of the package can be found at \url{http://code.google.com/p/cuda-insight-toolkit/}.
+The Examples subdirectory in the citk distribution includes a
+CMakeFile for building all examples and running tests. Location of the
+patched ITK, nvcc and CUDA SDK must be provided during configuration.
 
@@
   images. See {\em simple\_perf\_test.cxx} for details.
-\item Image filtering with kernels, for example simple means, offer ??
-  for 3d kernels, radius 10 voxels on images size $500 \times 500
-  \times 500$. This is potentially interesting for applications
-  requiring kernels of specific shape, because most accelerated CPU
-  schemes can only implement a restricted range of shape kernels. The
-  accelerated CPU scheme used in this test uses a box filtering
-  approach that is limited to rectangular filters.
+\item Image filtering with kernels, for example simple means, offer 32
+  times speedup for 3d kernels, radius 10 voxels on images size $500
+  \times 500 \times 500$ and 50 times speedup for kernels radius
+  20.. This is potentially interesting for applications requiring
+  kernels of specific shape, because most accelerated CPU schemes can
+  only implement a restricted range of shape kernels. Neither CPU nor
+  GPU examples exploits redundancy in this test.
 \end{itemize}

### 2011-05-20 trunk/CITK/Code/Common/itkCudaImportImageContainer.h
removed CITK subfolders - these are now managed at github

@@ -1,259 +1,0 @@
-/*=========================================================================
-
-Program:   Insight Segmentation & Registration Toolkit
-Module:    $RCSfile: itkImportImageContainer.h,v $
-Language:  C++
-Date:      $Date: 2009-04-25 12:24:09 $
-Version:   $Revision: 1.24 $
-
-Copyright (c) Insight Software Consortium. All rights reserved.
-See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
-
-This software is distributed WITHOUT ANY WARRANTY; without even 
-the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR 
-PURPOSE.  See the above copyright notices for more information.
-
-=========================================================================*/
-#ifndef __itkCudaImportImageContainer_h
-#define __itkCudaImportImageContainer_h
-
-#include "itkObject.h"
-#include "itkObjectFactory.h"
-#include "itkImportImageContainer.h"
-#include <cutil_inline.h>
-#include <utility>
-
-namespace itk
-{
-
-   /** \class ImportImageContainer
-    * Defines an itk::Image front-end to a standard C-array. This container
-    * conforms to the ImageContainerInterface. This is a full-fleged Object,
-    * so there is modification time, debug, and reference count information.
-    *
-    * Template parameters for ImportImageContainer:
-    *
-    * TElementIdentifier =
-    *     An INTEGRAL type for use in indexing the imported buffer.
-    *
-    * TElement =
-    *    The element type stored in the container.
-    *
-    * \ingroup ImageObjects
-    * \ingroup IOFilters
-    */
-
-   template <typename TElementIdentifier, typename TElement>
-      class CudaImportImageContainer:  
-         public ImportImageContainer <TElementIdentifier, TElement>
-   {
-      public:
-         /** Standard class typedefs. */
-         typedef CudaImportImageContainer  Self;
-         typedef ImportImageContainer<TElementIdentifier, TElement>      Superclass;
-         typedef SmartPointer<Self>        Pointer;
-         typedef SmartPointer<const Self>  ConstPointer;
-
-         /** Save the template parameters. */
-         typedef TElementIdentifier  ElementIdentifier;
-         typedef TElement            Element;
-
-         /** Method for creation through the object factory. */
-         itkNewMacro(Self);
-
-         /** Standard part of every itk Object. */
-         itkTypeMacro(CudaImportImageContainer, ImportImageContainer);
-
[…]

### 2011-05-20 trunk/CITK/Code/Common/itkImage.h

@@ -1,330 +1,0 @@
-/*=========================================================================
-.
-  Program:   Insight Segmentation & Registration Toolkit
-  Module:    $RCSfile: itkImage.h,v $
-  Language:  C++
-  Date:      $Date: 2009-08-14 13:28:21 $
-  Version:   $Revision: 1.151 $
-
-  Copyright (c) Insight Software Consortium. All rights reserved.
-  See ITKCopyright.txt or http://www.itk.org/HTML/Copyright.htm for details.
-
-     This software is distributed WITHOUT ANY WARRANTY; without even
-     the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR
-     PURPOSE.  See the above copyright notices for more information.
-
-=========================================================================*/
-#ifndef __itkImage_h
-#define __itkImage_h
-
-#include "itkImageBase.h"
-#include "itkImageRegion.h"
-#include "itkCudaImportImageContainer.h"
-#include "itkImportImageContainer.h"
-#include "itkDefaultPixelAccessor.h"
-#include "itkDefaultPixelAccessorFunctor.h"
-#include "itkPoint.h"
-#include "itkFixedArray.h"
-#include "itkWeakPointer.h"
-#include "itkNeighborhoodAccessorFunctor.h"
-
-namespace itk
-{
-/** \class Image
- *  \brief Templated n-dimensional image class.
- *
- * Images are templated over a pixel type (modeling the dependent
- * variables), and a dimension (number of independent variables).  The
- * container for the pixel data is the ImportImageContainer.
- *
- * Within the pixel container, images are modeled as arrays, defined by a
- * start index and a size.
- *
- * There are three sets of meta-data describing an image. These are "Region"
- * objects that define a portion of an image via a starting index for the image
- * array and a size. The ivar LargestPossibleRegion defines the size and
- * starting index of the image dataset. The entire image dataset, however,
- * need not be resident in memory. The region of the image that is resident in
- * memory is defined by the "BufferedRegion". The Buffer is a contiguous block
- * of memory.  The third set of meta-data defines a region of interest, called
- * the "RequestedRegion". The RequestedRegion is used by the pipeline
- * execution model to define what a filter is requested to produce.
- *
- * [RegionIndex, RegionSize] C [BufferIndex, BufferSize]
- *                           C [ImageIndex, ImageSize]
- *
[…]

### 2011-05-20 trunk/article/Article.tex
minor extras in article - sending to other authors

@@
 of some sample filters.
+\subsection{Fetch this contribution from google code}
+The source code is included with this article and is also available from google code:
+\url{http://code.google.com/p/cuda-insight-toolkit/}. The patch for ITK is included.
+
 \subsection{Patch ITK 3.20}
@@
 \item cd ITK-3.20
-\item patch -p0 $<$ path/to/patch.3.20.0.dif
+\item patch -p0 $<$ path/to/cuda-insight-toolkit/patch.3.20.0.dif
 \end{itemize}
@@
 \begin{itemize}
-  \item Specify location of CUDA SDK.
+  \item Specify location of CUDA SDK. Note that if there is trouble locating libcutil.a, it may be set explicitly under advanced options - CUDA\_CUT\_LIBRARY.
   \item Turn off SSE options for VNL - see advanced/VNL. This avoids errors caused by multiple inclusion of SSE files.
+  \item Enable ITK\_USE\_REVIEW under advanced options, in order to build all of the tests.
 \end{itemize}

### 2011-05-20 trunk/article/Article.tex
fixed arrows

@@
 CudaImageToImageFilter}. These filters allow the standard allocation
-structure to be used via {\em this->AllocateOutputs()}. Explicit
+structure to be used via {\em this$\rightarrow$AllocateOutputs()}. Explicit
 allocation of device memory can be achieved using
-{\em Image->AllocateGPU()}
+{\em Image$\rightarrow$AllocateGPU()}
 

### 2011-05-24 article/Article.tex
minor extras in article - sending to other authors
allowed cuda to be switched off for IJ

@@
 CMakeFile for building all examples and running tests. Location of the
-patched ITK, nvcc and CUDA SDK must be provided during configuration.
+patched ITK, nvcc and CUDA SDK must be provided during
+configuration. It is also necessary to set CITK\_USE\_CUDA to ON. This
+option has been included to allow the Insight Journal to run some
+tests without requiring CUDA development tools.
 

### 2011-08-07 article/Article.tex
Small corrections and author modification.

@@
 
+\newcommand{\IJhandlerIDnumber}{3269}
+
 % Increment the release number whenever significant changes are made.
@@
 \author{Richard Beare{$^1$}, Daniel Micevski, Chris Share\\Luke
-  Parkinson, Phil Ward, Wojtek Goscinski{$1$}, Mike Kuiper{$^2$}}
-\authoraddress{{$^1$}Richard.Beare@monash.edu, Monash University, Melbourne, Australia\\
-{$^2$}mike@vpac.org, Victorian Partnership for Advanced Computing, Melbourne, Australia.}
+  Parkinson, Phil Ward{$^2$}, Wojtek Goscinski{$1$}, Mike Kuiper{$^3$}}
+\authoraddress{{$^1$}Richard.Beare@monash.edu, Monash University, Melbourne, Australia.\\
+{$^2$}P.ward@csiro.au, CSIRO Land and Water, Highett, Australia.\\
+{$^3$}mike@vpac.org, Victorian Partnership for Advanced Computing, Melbourne, Australia.}
 
 \begin{document}
+\IJhandlefooter{\IJhandlerIDnumber}
 \maketitle
@@
 through an iterator, the {\em CudaImportImageContainer} checks whether
-the most up to date image is on the device or the host. If it is on
+the most up-to-date image is on the device or the host. If it is on
 the device, it is copied back onto the host. This data is then
 supplied to the user. Similarly when a GPU filter requests the image
-data, the {\em CudaImportImageContainer} would check where the most up
-to date image is, and copy it to the device if required.
+data, the {\em CudaImportImageContainer} would check where the most 
+up-to-date image is, and copy it to the device if required.
 
@@
 The result of this is memory transfers are only performed when
-required and are completed transparent to both the developer and the
+required and are completely transparent to both the developer and the
 user. This leaves all the responsibility on the architect, rather than
-the developer or the user such as in the other attempts.
+the developer or the user such as in the other GPU implementations.
 
@@
 \section{Anatomy of a CUDA enabled filter}
-CUDA enabled filters can look very like a conventional ITK filter,
+CUDA enabled filters resemble a conventional ITK filter for the most part,
 with the main difference being a call to a CUDA kernel function from
@@
   portion of ITK is CUDA (or GPU) enabled. Therefore a developer will
-  only experience a nett performance gain if the CUDA enabled filter
+  only experience a net performance gain if the CUDA enabled filter
   offers sufficient speedup to offset memory transfer costs and a
@@
   \times 500 \times 500$ and 50 times speedup for kernels radius
-  20.. This is potentially interesting for applications requiring
+  20. This is potentially interesting for applications requiring
   kernels of specific shape, because most accelerated CPU schemes can

### 2011-08-24 article/Article.tex
changed email to upper case

@@
 \authoraddress{{$^1$}Richard.Beare@monash.edu, Monash University, Melbourne, Australia.\\
-{$^2$}P.ward@csiro.au, CSIRO Land and Water, Highett, Australia.\\
+{$^2$}P.Ward@csiro.au, CSIRO Land and Water, Highett, Australia.\\
 {$^3$}mike@vpac.org, Victorian Partnership for Advanced Computing, Melbourne, Australia.}
